### 2024-10-29 paper/paper.qmd
**Data Overview** part finished in paper.qmd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Chenming Zhao
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder).
        We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis. The data is available at: [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

Polling data for the 2024 U.S. presidential election is provided by FiveThirtyEight [@fivethirtyeight]. This dataset compiles information from numerous polls conducted by various pollsters, detailing public support levels for presidential candidates. This data is periodically updated on FiveThirtyEight's website to reflect the latest polling information for the 2024 election. Each record includes information we need like state in which the poll was conducted (if applicable), polling dates (start and end), the specific pollster, the sample size of each poll, the polling methodology (such as phone, online, etc.), and support percentages for each candidate. This dataset serves as the foundation for analyzing trends and building predictive models for the winner of the upcoming US presidential election. Table tbl-pollingdata below previews this information for polls conducted in 2023 and 2024.

To simulate, test, analyze, and clean the polling data, the statistical programming language R was employed [@citeR]. Key libraries that supported the data analysis include `tidyverse` [@tidyverse], `dplyr` [@dplyr], `ggplot2` [@ggplot2], and `broom` [@broom] for tidying model outputs. Additionally, the `rstanarm` [@rstanarm] library was utilized to implement multilevel modeling for prediction purposes.

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

\newpage

# References

### 2024-10-29 paper/paper.tex
**Data Overview** part finished in paper.qmd

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{rotating}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Chenming Zhao},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
\url{https://github.com/RohanAlexander/starter_folder}. We gratefully
acknowledge FiveThirtyEight for providing the polling data used in this
analysis. The data is available at:
\url{https://projects.fivethirtyeight.com/polls/president-general/2024/national/}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{Chenming Zhao}
\date{October 28, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}

\section{Introduction}\label{introduction}

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as
follows. Section~\ref{sec-data}\ldots.

\section{Data}\label{sec-data}

\subsection{Overview}\label{overview}

Polling data for the 2024 U.S. presidential election is provided by
FiveThirtyEight (FiveThirtyEight 2024). This dataset compiles
information from numerous polls conducted by various pollsters,
detailing public support levels for presidential candidates. This data
is periodically updated on FiveThirtyEight's website to reflect the
latest polling information for the 2024 election. Each record includes
information we need like state in which the poll was conducted (if
applicable), polling dates (start and end), the specific pollster, the
sample size of each poll, the polling methodology (such as phone,
online, etc.), and support percentages for each candidate. This dataset
serves as the foundation for analyzing trends and building predictive
models for the winner of the upcoming US presidential election. Table
tbl-pollingdata below previews this information for polls conducted in
2023 and 2024.

To simulate, test, analyze, and clean the polling data, the statistical
programming language R was employed (R Core Team 2023). Key libraries
that supported the data analysis include \texttt{tidyverse}
(\textbf{tidyverse?}), \texttt{dplyr} (Wickham et al. 2023),
\texttt{ggplot2} (Wickham 2016), and \texttt{broom} (Robinson, Hayes,
and Couch 2024) for tidying model outputs. Additionally, the
\texttt{rstanarm} (Goodrich et al. 2022) library was utilized to
implement multilevel modeling for prediction purposes.

\subsection{Measurement}\label{measurement}

Some paragraphs about how we go from a phenomena in the world to an
entry in the dataset.

\subsection{Outcome variables}\label{outcome-variables}

Add graphs, tables and text. Use sub-sub-headings for each outcome
variable or update the subheading to be singular.

Some of our data is of penguins (Figure~\ref{fig-bills}), from Horst,
Hill, and Gorman (2020).

\begin{figure}

\centering{

\includegraphics{paper_files/figure-pdf/fig-bills-1.pdf}

}

\caption{\label{fig-bills}Bills of penguins}

\end{figure}%

Talk more about it.

And also planes (fig-planes). (You can change the height and width, but
don't worry about doing that until you have finished every other aspect
of the paper - Quarto will try to make it look nice and the defaults
usually work well once you have enough text.)

Talk way more about it.

\subsection{Predictor variables}\label{predictor-variables}

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine
a few into one if they go together naturally.

\section{Model}\label{model}

The goal of our modelling strategy is twofold. Firstly,\ldots{}

Here we briefly describe the Bayesian analysis model used to
investigate\ldots{} Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\subsection{Model set-up}\label{model-set-up}

Define \(y_i\) as the number of seconds that the plane remained aloft.
Then \(\beta_i\) is the wing width and \(\gamma_i\) is the wing length,
both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\subsubsection{Model justification}\label{model-justification}

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

\section{Results}\label{results}

Our results are summarized in Table~\ref{tbl-modelresults}.

\begin{table}

\caption{\label{tbl-modelresults}Explanatory models of flight time based
on wing width and wing length}

\centering{

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
hline{8}={1,2}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
& First model \\ \midrule %% TinyTableHeader
(Intercept) & \num{1.12}    \\
& (\num{1.70})  \\
length      & \num{0.01}    \\
& (\num{0.01})  \\
width       & \num{-0.01}   \\
& (\num{0.02})  \\
Num.Obs.    & \num{19}      \\
R2          & \num{0.320}   \\
R2 Adj.     & \num{0.019}   \\
Log.Lik.    & \num{-18.128} \\
ELPD        & \num{-21.6}   \\
ELPD s.e.   & \num{2.1}     \\
LOOIC       & \num{43.2}    \\
LOOIC s.e.  & \num{4.3}     \\
WAIC        & \num{42.7}    \\
RMSE        & \num{0.60}    \\
\bottomrule
\end{tblr}

}

\end{table}%

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

Please don't use these as sub-heading labels - change them to be what
your point actually is.

\subsection{Third discussion point}\label{third-discussion-point}

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\subsection{Posterior predictive
check}\label{posterior-predictive-check}

In fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive
check. This shows\ldots{}

In fig-ppcheckandposteriorvsprior-2 we compare the posterior with the
prior. This shows\ldots{}

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-fivethirtyeight}
FiveThirtyEight. 2024. {``{2024 Presidential General Election Polls}.''}
\url{https://projects.fivethirtyeight.com/polls/president-general/2024/national/}.

\bibitem[\citeproctext]{ref-rstanarm}
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
\url{https://mc-stan.org/rstanarm/}.

\bibitem[\citeproctext]{ref-palmerpenguins}
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
\emph{{palmerpenguins: Palmer Archipelago (Antarctica) penguin data}}.
\url{https://doi.org/10.5281/zenodo.3960218}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-broom}
Robinson, David, Alex Hayes, and Simon Couch. 2024. \emph{Broom: Convert
Statistical Objects into Tidy Tibbles}.
\url{https://broom.tidymodels.org/}.

\bibitem[\citeproctext]{ref-ggplot2}
Wickham, Hadley. 2016. \emph{Ggplot2: Elegant Graphics for Data
Analysis}. Springer-Verlag New York.
\url{https://ggplot2.tidyverse.org}.

\bibitem[\citeproctext]{ref-dplyr}
Wickham, Hadley, Romain François, Lionel Henry, Kirill Müller, and Davis
Vaughan. 2023. \emph{Dplyr: A Grammar of Data Manipulation}.
\url{https://dplyr.tidyverse.org}.

\end{CSLReferences}

\end{document}

### 2024-10-29 paper/paper.qmd
data overview part draft1 done

@@
 
-And also planes (fig-planes).
+And also planes (@fig-planes).
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+
+```{r}
+#| label: fig-planes
+#| fig-cap: Relationship between wing length and width
+#| echo: false
+#| warning: false
+#| message: false
+
+analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+
+analysis_data |> 
+  ggplot(aes(x = width, y = length)) +
+  geom_point(alpha = 0.8) +
+  theme_minimal() +
+  labs(x = "Wing width (mm)",
+       y = "Wing length (mm)")
+```
 
@@
 
-In fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
 
-In fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the model fits, and is affected by, the data"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
+
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(first_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
+## Diagnostics
+
+@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+
+@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+
+plot(first_model, "trace")
+
+plot(first_model, "rhat")
+```
 

### 2024-10-30 scripts/00-simulate_data.R
1. sketches uploaded. 2. data simulated and saved 3. test for simulation done, all passed 4. analysis data updated and cleaned 5. deleted files that we do not need

@@ -1,52 +1,53 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of America 2024 presidential polls, including the 
+#          state, pollster, methodology, support rate, and other relevant fields.
+# Author: Chenming Zhao
+# Date: 26 October 2024
+# Contact: chenming.zhao@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
+# Pre-requisites: The `tidyverse` and `lubridate` packages must be installed.
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+library(lubridate)
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+set.seed(853)
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+# function that give random date from 2024-07-21 to 2024-11-05
+random_dates <- function(n) {
+  start_date <- as.Date("2024-07-21")
+  end_date <- as.Date("2024-11-04")
+  date_seq <- seq(start_date, end_date, by = "day")
+  sampled_dates <- sample(date_seq, size = n, replace = TRUE)}
 
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
+# simulate data
+political_support <-
+  tibble(
+    start_date = random_dates(1000),
+    state = sample(c("Alabama", "Alaska", "Arkansas", "California", "Colorado", 
[…]

### 2024-10-30 scripts/01-test_simulated_data.R

@@ -1,9 +1,8 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated America 2024 presidential polls dataset
+# Author: Chenmming Zhao
+# Date: 26 October 2024
+# Contact: chenming.zhao@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
@@ -14,7 +13,7 @@
 #### Workspace setup ####
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+sample_data <- read_csv("/cloud/project/data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
 if (exists("analysis_data")) {
@@ -23,67 +22,71 @@ if (exists("analysis_data")) {
   stop("Test Failed: The dataset could not be loaded.")
 }
 
-
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Check if the dataset has 1000 rows
+if (nrow(sample_data) == 1000) {
+  message("Test Passed: The dataset has 1000 rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The dataset does not have 1000 rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Check if the dataset has 8 columns
+if (ncol(sample_data) == 8) {
+  message("Test Passed: The dataset has 8 columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The dataset does not have 8 columns.")
 }
 
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
+# Check if all values in the 'start_date' column are reasonable
+if (all(as.Date("2024-07-21") <= sample_data$start_date & as.Date("2024-11-04") >= sample_data$start_date)) {
[…]

### 2024-10-30 scripts/02-clean_data.R

@@ -1,5 +1,7 @@
 #### Preamble ####
-# Purpose: Cleans and preprocesses raw polling data for the 2024 US presidential election.
+# Purpose: Cleans and preprocesses raw polling data for the 2024 US presidential election
+#          and combined with 2023 economic situation (GDP and personal income) national in
+#          U.S. and per state.
 #          The data includes national polling results from various pollsters, as well as
 #          details on methodology, sample size, and polling dates. This script aims to
 #          clean and structure the data for analysis and model building.
@@ -18,19 +20,25 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(readxl)
 library(dplyr)
 
 #### Clean data ####
 raw_data <- read_csv("/cloud/project/data/01-raw_data/president_polls_raw_data.csv")
 
-# Filters were used to filter Trump approval ratings in the dataset
+
+# Filters were used to filter good quality Trump related polls in the dataset
 trump_data <- raw_data %>%
-  filter(candidate_name == "Donald Trump")
+  mutate(candidate_name = str_replace(candidate_name, " Jr.", "")) %>%
+  mutate(start_date = as.Date(start_date, format = "%m/%d/%y")) %>%
+  mutate(end_date = as.Date(end_date, format = "%m/%d/%y")) %>%
+  # We only consider polls results after Biden's Withdrawal
+  filter(candidate_name == "Donald Trump" &  numeric_grade >= 2.7 & start_date >= as.Date("2024-07-21")) %>%
+  distinct()
 
 # Delete NAs in pollster column
 trump_data <- trump_data %>%
   filter(!is.na(pollster))
-
 
 # calculate the mean of pct and sample_size (NA values excluded)
 mean_pct <- mean(trump_data$pct, na.rm = TRUE)
@@ -45,16 +53,23 @@ trump_data$pct[trump_data$pct < 0] <- 0
 # Set the pct values greater than 100 to 100
 trump_data$pct[trump_data$pct > 100] <- 100
 
-trump_data <- trump_data %>%
-  select(state, pollster, methodology, sample_size, pct)
-
 # Fill the missing state and methodology with "unknown" so that they can participate in the layering of the model.
 trump_data <- trump_data %>%
   mutate(
-    state = ifelse(is.na(state), "unknown", state),
+    state = ifelse(is.na(state), "national", state),
[…]

### 2024-10-30 scripts/05-exploratory_data_analysis.R

@@ -13,25 +13,25 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+trump_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+
+# 构建贝叶斯模型，加入时间趋势（随机游走）
+trump_time_series_model <- stan_glmer(
+  pct ~ methodology + days_since_start + is_national + (1 + days_since_start | state) + (1 | pollster), 
+  data = trump_data, 
+  family = gaussian(),
+  prior = normal(0, 10, autoscale = TRUE),
+  prior_intercept = normal(50, 10, autoscale = TRUE),
+  prior_covariance = decov(regularization = 2)
+)
 
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  trump_time_series_model,
+  file = "/cloud/project/models/trump_time_model.rds"
 )
 
 

### 2024-10-30 scripts/06-model_data.R

@@ -7,31 +7,28 @@
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
 
-
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+trump_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+trump_time_series_model <- stan_glmer(
+  pct ~ methodology + days_since_Biden_Withdrawal + is_national + (1 | state) + (1 + days_since_Biden_Withdrawal | pollster), 
+  data = trump_data, 
+  family = gaussian(),
+  prior = normal(0, 10, autoscale = TRUE),
+  prior_intercept = normal(50, 10, autoscale = TRUE),
+  prior_covariance = decov(regularization = 2)
+)
 
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  trump_time_series_model,
+  file = "/cloud/project/models/trump_time_model.rds"
 )
 
 

### 2024-10-30 scripts/04-prior_simulation.R
1. file names changed to show correct order 2. prior simulation done 3. model created and fitted

@@ -1,0 +1,107 @@
+#### Preamble ####
+# Purpose: Model Trump's support rate in the 2024 U.S. Presidential Election
+# Author: Chenming Zhao
+# Date: 30 October 2024
+# Contact: chenming.zhao@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: This script requires access to simulated prior distributions 
+#                 for Trump's support rate, based on factors such as days since 
+#                 Biden's withdrawal, pollster effects, methodology, and state/national indicators.
+#                 Make sure to have 'tibble', 'ggplot2', and 'dplyr' libraries installed.
+# Overview:This script is designed to set up prior distributions for Bayesian modeling 
+#          of Trump's support rate in the 2024 election. The factors influencing support rate 
+#          (as captured in this simulation) include:
+#          - Methodology (method of polling),
+#          - Days since Biden's withdrawal,
+#          - National or state-level effect,
+#          - Pollster (random effect including time influence),
+#          - State-level effects.
+#          The purpose of these priors is to assess the model's predictions before fitting actual data, 
+#          ensuring reasonable assumptions about the ranges and distributions for each variable. 
+#          These checks provide insight into whether the priors are likely to yield interpretable 
+#          and realistic results once data is introduced.
+
+
+#### Workspace setup ####
+library(tibble)
+library(ggplot2)
+library(dplyr)
+
+# Set the prior parameters of the simulation
+draws <- 1000
+num_effects <- 16
+
+# Time range: Shorten the range of days and repeat to ensure consistent column length
+time_range <- rep(seq(0, 100, by = 5), length.out = draws * num_effects)
+
+priors <- tibble(
+  sigma = rep(rexp(n = draws, rate = 1), times = num_effects),
+  # Intercept prior
+  beta_0 = rep(rnorm(n = draws, mean = 40, sd = 2.5), times = num_effects),
+  
+  # days_since_Biden_Withdrawal prior
+  beta_time = rep(rnorm(n = draws, mean = 0, sd = 0.2), times = num_effects),
+  
+  # pollster effect prior
+  beta_pollster = rep(rnorm(n = draws, mean = 0, sd = 1), times = num_effects),
+  
+  # methodology effect prior
[…]

### 2024-10-30 scripts/05-exploratory_data_analysis.R

@@ -1,37 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-
-#### Read data ####
-trump_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
-
-### Model data ####
-
-# 构建贝叶斯模型，加入时间趋势（随机游走）
-trump_time_series_model <- stan_glmer(
-  pct ~ methodology + days_since_start + is_national + (1 + days_since_start | state) + (1 | pollster), 
-  data = trump_data, 
-  family = gaussian(),
-  prior = normal(0, 10, autoscale = TRUE),
-  prior_intercept = normal(50, 10, autoscale = TRUE),
-  prior_covariance = decov(regularization = 2)
-)
-
-
-#### Save model ####
-saveRDS(
-  trump_time_series_model,
-  file = "/cloud/project/models/trump_time_model.rds"
-)
-
-

### 2024-10-30 scripts/05-model_data.R

@@ -1,0 +1,34 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+
+#### Read data ####
+trump_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
+
+### Model data ####
+trump_time_series_model <- stan_glmer(
+  pct ~ methodology + days_since_Biden_Withdrawal + is_national + (1 | state) + (1 + days_since_Biden_Withdrawal | pollster), 
+  data = trump_data, 
+  family = gaussian(),
+  prior = normal(0, 5, autoscale = TRUE),
+  prior_intercept = normal(45, 5, autoscale = TRUE),
+  prior_covariance = decov(regularization = 1)
+)
+
+
+#### Save model ####
+saveRDS(
+  trump_time_series_model,
+  file = "/cloud/project/models/trump_time_model.rds"
+)
+
+

### 2024-10-30 scripts/06-model_data.R

@@ -1,34 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-
-#### Read data ####
-trump_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
-
-### Model data ####
-trump_time_series_model <- stan_glmer(
-  pct ~ methodology + days_since_Biden_Withdrawal + is_national + (1 | state) + (1 + days_since_Biden_Withdrawal | pollster), 
-  data = trump_data, 
-  family = gaussian(),
-  prior = normal(0, 10, autoscale = TRUE),
-  prior_intercept = normal(50, 10, autoscale = TRUE),
-  prior_covariance = decov(regularization = 2)
-)
-
-
-#### Save model ####
-saveRDS(
-  trump_time_series_model,
-  file = "/cloud/project/models/trump_time_model.rds"
-)
-
-

### 2024-10-30 paper/paper.qmd
first version of data part in paper completed. plots need better format and have some minor errors like citation

@@
 library(tidyverse)
-library(palmerpenguins)
+library(dplyr)
+library(knitr)
+library(ggplot2)
 ```
@@
 To simulate, test, analyze, and clean the polling data, the statistical programming language R was employed [@citeR].
-Key libraries that supported the data analysis include `tidyverse` [@tidyverse], `dplyr` [@dplyr], `ggplot2` [@ggplot2], and `broom` [@broom] for tidying model outputs.
+Key libraries that supported the data analysis include `tidyverse` [@tidyverse], `readxl` [@readxl], `dplyr` [@dplyr], `knitr` [@knitr], `ggplot2` [@ggplot2], and `broom` [@broom] for tidying model outputs.
 Additionally, the `rstanarm` [@rstanarm] library was utilized to implement multilevel modeling for prediction purposes.
+Also this analysis inherits the folder structure from Professor Rohan Alexander from University of Toronto [@rohan].
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The process of transforming real-world phenomena into structured data typically involves several critical steps, from designing surveys to final data entry.
+First, we identify what needs to be measured.
+In this case, we focus on public opinion regarding the 2024 presidential election, particularly support rates for various candidates.
+It is essential to define the data scope (e.g., national or state level) and key variables—such as polling information (e.g., polling organization, start and end dates), sample details (e.g., sample size and demographics), and candidate details (e.g., candidate name and party affiliation).
 
-## Outcome variables
+Next, polling organizations develop survey questions based on the desired data, considering sample size, sampling methods, and survey modes to capture respondents' preferences and voting intentions.
+Different methodologies impact the results, as they reflect the views of distinct groups, which may be influenced by factors like access channels, demographics, and technology usage.
+For instance, face-to-face surveys tend to capture opinions from offline-inclined groups, whereas voluntary online surveys exclude those less active online【cite】.
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+Once the survey is designed, polling begins, and responses are aggregated by the polling organization.
+Respondents' answers are recorded and categorized, converting their opinions into structured data points, though these lack the nuances of human complexity.
+To protect privacy, data are often anonymized and aggregated, retaining key insights.
+After collection, raw data undergo cleaning and processing to minimize sampling biases and errors.
+Yet, any single poll can have random and systematic error sources, so combining multiple poll results helps mitigate these errors【cite】.
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+Processed data are entered into structured datasets.
+Ideally, well-formatted polling data are stored as individual records, typically including fields like polling organization, sample size, survey dates, margin of error, candidate support percentages, and methodology description.
+On platforms like FiveThirtyEight, these fields are standardized for ease of comparison and analysis.
+Finally, FiveThirtyEight and similar platforms aggregate these structured records and present them to the public or allow non-commercial research use, with data usually updated as new polls are released.
+This enables analysts and the public to track changes in candidate support, analyze trends, and interpret results.
+An interesting phenomenon, however, is that as election day approaches, poll results often "converge" or "follow" the average, reducing polling error, with evidence suggesting some "final adjustments" in methodology may occur【cite】.
+
+## Analysis Data
+This analysis is focused on Donald Trump, so we only collected observations where the candidate_name is Trump.
+At the same time, we prioritize the quality of the polls.
+In a political approval rate prediction model, which is often influenced by numerous complex factors, we encounter data that is typically complex and noisy.
+Low-quality poll results can introduce significant bias into our prediction model, further impacting the accuracy of inferences.
+Therefore, only polls with a numeric_grade above 2.7 were selected.
+Additionally, Trump's main opponent, Kamala Harris, only entered the race after Biden’s withdrawal, a major political event that could have significant effects on the support rates for both sides.
+As such, we focused solely on polls conducted after Biden’s withdrawal to enhance the model’s prediction accuracy for the final outcome.
+
+In researching the likelihood of Trump winning, we selected specific variables to focus on those most impactful for predicting approval rates.
+Here is an overview of data used for this analysis @tbl-view.
+Following are selected ourcome variables and predictor variables, and explainations respectively.
+
+### Outcome variables
+In this analysis of Donald Trump’s support rate in the 2024 U.S.
+presidential election, the outcome variable is Trump’s support rate (pct) because it is directly related to the election results.
+The primary research goal of this analysis is to predict Trump’s chances of winning in the 2024 election, so the support rate is the main metric we aim to model and forecast.
+The support rate represents the proportion of respondents in a specific poll who support Trump.
+We seek to understand how the support rate is influenced by different factors, such as polling methodology, time, or geographical variables.
+By modeling the fluctuations in Trump’s support rate, we can infer his electoral performance, analyze the trends within his support base, and assess the impact of various factors on his popularity.
+Understanding these dynamics provides insights into Trump’s standing relative to his opponents and supports our overall election prediction.
+
+### Predictor variables
+In this analysis, the predictor variables are the factors that we believe can influence the support rate for Trump.
+These variables are chosen based on their potential to explain changes in support rate.
+Following are the predictor variables that will be included in our model, along with an explanation of their significance.
+
+**start_date**: Public sentiment and approval rates fluctuate dynamically during an election period, influenced by the passage of time, major events, and campaign strategies.
+By recording the date of each poll, we can observe changes in support over time.
+
+**state/national**: Political environments and voter preferences may vary significantly by state, and national polls cannot fully reflect conditions in individual states.
+The electoral college system in the U.S.
+makes state-level approval rates crucial for predicting the likelihood of winning.
+
+**pollster**: Different polling organizations use varying survey methods, sampling strategies, and data-processing procedures, which impact the reliability and accuracy of the poll results.
+Knowing which polling organization published the data helps assess potential biases in the data.
+
+**methodology**: Different survey methods (e.g., telephone interviews, online questionnaires) significantly impact the representativeness of the results, as they directly influence the characteristics of the sampled population.
+Some methods may introduce biases toward specific demographic groups; for example, telephone surveys may skew toward older demographics, while online surveys may skew toward younger ones.
+
+**is_national**: This variable helps us distinguish between national and state-level polls, ensuring the model can adapt and adjust across different geographic levels.
+
+**days_since_Biden_Withdrawal**: Trump's main opponent, Kamala Harris, entered the race only after Biden withdrew.
+Major political events like Biden’s withdrawal can significantly impact voter approval rates, and tracking the time since this event helps assess both its short-term and long-term effects.
+
+Other potential variables (such as voter demographics like gender, age, race, and income) could indeed influence voter approval rates, but they primarily pertain to a **micro-level** analysis.
+After incorporating GDP and per capita income data from various U.S.
+states and nationwide in 2023 into a generalized linear model, we found that their correlation with presidential election outcomes was not very strong, likely due to data limitations in capturing the effect of economic changes on the election.
+Thus, we did not include these factors.
+Additionally, individual voter characteristics (such as gender and education level) are not consistently available in most polls.
+In comparison, the variables we chose are more complete and comprehensively capture the macro nature of the data.
+Therefore, selecting these variables allows us to maintain data simplicity while maximizing the capture of key factors influencing approval rates, avoiding the noise introduced by excessive micro-level variables.
+
+```{r, message=FALSE}
+analysis_data <- read_csv(here::here("/cloud/project/data/02-analysis_data/analysis_trump_data.csv"))
+```
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: tbl-view
+#| tbl-cap: The First Few Lines of Cleaned Analysis Data
 #| echo: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+kable(head(analysis_data, 10), 
+      col.names = c("start_date", "state/national", "pollster", "methodology", "Trump Support Rate", "is_national", "days_since_Biden_Withdrawal"), 
+      align = c("l", "c", "c", "c", "c", "c", "c"))
 ```
 
-Talk more about it.
+### Figures
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+The following figures, @fig-pollstermetho, @fig-state and @fig-overtime, display various aspects of data related to Trump's support rate, helping us understand how support rates vary with different factors.
+In @fig-pollstermetho and @fig-state, we have marked the occurrence count of each pollster or state on the x-axis, helping us identify potential sources of bias in the data.
+Low-frequency items (such as data points from certain pollsters or states) may reduce the representativeness of the model—low-frequency observations imply insufficient data for specific pollsters or states, which may not accurately reflect voter support rates in these areas.
+This incomplete data could lead to unreliable predictions for these pollsters or states, increasing prediction errors.
+Additionally, low-frequency data is more susceptible to extreme values.
+With fewer observations, certain outlier data points (e.g., a particularly high or low support rate in a single poll) can appear disproportionately significant, affecting the overall prediction.
+When fitting the model to low-frequency data, it may be more influenced by the "noise" in these data points, potentially introducing bias into the overall results.
+Systematic biases in low-frequency observations could spread throughout the model, impacting the overall accuracy of the predictions.
 
+Although low-frequency observations may introduce some bias, directly removing them would result in information loss, especially in election predictions where the representativeness of different states and pollsters is crucial.
+Different pollsters and states have their own resources and priorities, leading to uneven data coverage.
+Some pollsters may prefer to publish data at specific times, while certain states, due to smaller populations or stable voter behavior, may receive less attention.
+Thus, it is challenging to completely balance the data quantity across different items.
+Although some observations have low frequency, they still contain valuable information.
+For instance, even though smaller or remote states may have limited data, their voter preferences are still significant under the Electoral College system.
+Completely deleting these observations would diminish these states' representation in the overall analysis, weakening the model's accuracy in reflecting support rates.
+Additionally, we aim to cover as many pollsters and states as possible with the model, so we retain even low-frequency observations.
+Thus, we keep these observations and mitigate the bias they introduce by combining other variables to build a more comprehensive and robust predictive model.
+
+@fig-pollstermetho shows the average support rates for the top and bottom ten pollsters, highlighting each pollster’s most commonly used methodology.
+We can observe that the support rates between the top 5 and bottom 5 pollsters differ by about 10%, which helps us understand the bias introduced by certain pollsters’ influence on support rates, as some pollsters may tend to show higher or lower support rates.
+This chart also examines the different methodologies used by these pollsters, as varying survey methods (e.g., phone surveys or online panels) may affect the results by reaching different groups of voters.
+Focusing on these differences aids in assessing the reliability and bias of the data.
+
+@fig-state compares the average support rates across states with the national average, showing regional differences in voter preferences.
+Due to the Electoral College system in the U.S.
+presidential election, variations in state support rates can significantly impact the election outcome.
+This analysis highlights the differences between state and national polls, helping us understand Trump’s relative support in each state.
+Paying attention to geographic disparities improves the model's prediction accuracy.
+
+@fig-overtime displays the trend in support rates over time for the top five pollsters with the most observations.
+We chose these pollsters because a sufficient number of observations is needed to accurately capture trend changes and reduce the impact of extreme values.
+Each subplot represents a pollster and shows the change in Trump’s support rate since Biden’s withdrawal.
+This helps us observe the dynamic change in support rates following major events, and we can also see how different pollsters respond to the same event.
+Analyzing time trends aids in understanding shifts in public opinion, providing more time-sensitive support rate predictions.
+
+```{r, message=FALSE}
+#| label: fig-pollstermetho
+#| fig-cap: Support Rates for Donald Trump of Ten Pollsters with Their Most Common used Metholodogy
+#| echo: false
+
+### Group by top 5 and bottom 5 avg pct by pollsters and their most common methodology
+# count average pct and occurrence times for each pollster
+pollster_summary <- analysis_data %>%
+  group_by(pollster, methodology) %>%
+  summarize(
+    avg_pct = mean(pct, na.rm = TRUE),
+    count = n()
+  ) %>%
+  ungroup()
+
+# find pollsters with top 5 avg pct and bottom 5 avg pct
+top5_pollsters <- pollster_summary %>%
+  group_by(pollster) %>%
+  summarize(
+    avg_pct = mean(avg_pct),
+    count = sum(count)
+  ) %>%
+  arrange(desc(avg_pct)) %>%
+  slice_head(n = 5) %>%
+  mutate(category = "Top 5")
+
+bottom5_pollsters <- pollster_summary %>%
+  group_by(pollster) %>%
+  summarize(
+    avg_pct = mean(avg_pct),
+    count = sum(count)
+  ) %>%
+  arrange(avg_pct) %>%
+  slice_head(n = 5) %>%
+  mutate(category = "Bottom 5")
+
+# merge
+selected_pollsters <- bind_rows(top5_pollsters, bottom5_pollsters) %>%
+  select(pollster, category)
+
+# find most commonly used methodology 
+selected_pollster_data <- pollster_summary %>%
+  filter(pollster %in% selected_pollsters$pollster) %>%
+  group_by(pollster) %>%
+  filter(count == max(count)) %>%
+  ungroup() %>%
+  left_join(selected_pollsters, by = "pollster")
+
+ggplot(selected_pollster_data, aes(x = reorder(paste(pollster, "(", count, ")", sep = ""), -avg_pct), y = avg_pct, fill = methodology)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~ category, scales = "free_x") +
+  labs(
+    title = "Top 5 and Bottom 5 Avg Support Rate for Donald Trump",
+    subtitle = "With Most Common Used Methodologies of Each Pollsters",
+    x = "Pollster (Occurrence Count)",
+    y = "Average Support Rate (%)"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(size = 16, face = "bold", color = "#333333"),
+    axis.title = element_text(size = 14, color = "#333333")
+  ) +
+  scale_fill_brewer(palette = "Set3") # assign colors to different methodologies
+
+```
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-state
+#| fig-cap: Average Support Rate for Trump of Each Category Based on State
 #| echo: false
-#| warning: false
-#| message: false
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+### Group by avg pct of different states and national avg pct
+# count average pct and occurrence times for each state category
+state_summary <- analysis_data %>%
+  group_by(state) %>%
+  summarize(
+    avg_pct = mean(pct, na.rm = TRUE),
+    count = n()
+  ) %>%
+  ungroup()
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
+# find states with top 5 avg pct and bottom 5 avg pct plus national avg pct
+top5_state <- state_summary %>%
+  group_by(state) %>%
+  summarize(
+    avg_pct = mean(avg_pct),
+    count = sum(count)
+  ) %>%
+  arrange(desc(avg_pct)) %>%
+  slice_head(n = 5) %>%
+  mutate(category = "Top 5")
+
+bottom5_state <- state_summary %>%
+  group_by(state) %>%
+  summarize(
+    avg_pct = mean(avg_pct),
+    count = sum(count)
+  ) %>%
+  arrange(avg_pct) %>%
+  slice_head(n = 5) %>%
+  mutate(category = "Bottom 5")
+
+national <- state_summary %>%
+  group_by(state) %>%
+  filter(state == "national") %>%
+  summarize(
+    avg_pct = mean(avg_pct),
+    count = sum(count)
+  ) %>%
+  arrange(avg_pct) %>%
+  mutate(category = "national")
+
+# merge
+selected_states <- bind_rows(top5_state, bottom5_state, national) %>%
+  select(state, category)
+
+# find most commonly used methodology 
+selected_state_data <- state_summary %>%
+  filter(state %in% selected_states$state) %>%
+  group_by(state) %>%
+  ungroup() %>%
+  left_join(selected_states, by = "state")
+
+ggplot(selected_state_data, aes(x = reorder(paste(state, "(", count, ")", sep = ""), -avg_pct), y = avg_pct, fill = state)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~ category, scales = "free_x") +
+  labs(
+    title = "Average Support Rate for Doanld Trump by states",
+    subtitle = "National Average Support Rate Included",
+    x = "State Names or National (Occurrence Count)",
+    y = "Average Support Rate (%)"
+  ) +
   theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(size = 16, face = "bold", color = "#333333"),
+    axis.title = element_text(size = 14, color = "#333333")
+  ) +
+  scale_fill_brewer(palette = "Set3") # assign colors to different states
 ```
 
-Talk way more about it.
+```{r, message=FALSE}
+#| label: fig-overtime
+#| fig-cap: Trend for Average Support Rate for Donald Trump Over Time Since Joe Biden's Withdrawal on 2024 July 21
+#| echo: false
 
-## Predictor variables
+# Identify the top 10 pollsters by occurrence
+top_pollsters2 <- analysis_data %>%
+  count(pollster, sort = TRUE) %>%
+  top_n(5, n) %>%
+  pull(pollster)
 
-Add graphs, tables and text.
+data <- analysis_data %>%
+  filter(pollster %in% top_pollsters2)
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+# Assign colors for each pollster
+colors <- RColorBrewer::brewer.pal(n = 10, name = "Set3")
+
+### Time trend since Binden's Withdrawal
+support_trend_5day <- data %>%
+  mutate(grouped_days = (days_since_Biden_Withdrawal %/% 7) * 7) %>% # counted weekly to reduce effect by extreme values
+  group_by(grouped_days, pollster) %>%
+  summarize(avg_pct = mean(pct, na.rm = TRUE)) %>%
+  ungroup()
+
+# Step 2: Create the line plot with background distribution
+ggplot(support_trend_5day, aes(x = grouped_days, y = avg_pct)) +
+  geom_line(aes(color = pollster), linewidth = 1.2) + # Main line color
+  geom_jitter(data = data, aes(x = days_since_Biden_Withdrawal, y = pct), 
+              color = "#a6cee3", alpha = 0.4, width = 1, height = 0.5) +
+  scale_x_continuous(
+    breaks = seq(min(analysis_data$days_since_Biden_Withdrawal), 
+                 max(analysis_data$days_since_Biden_Withdrawal), 
+                 by = 14)
+  ) +
+  labs(
+    title = "Average Support Rate for Donald Trump Over Time",
+    subtitle = "Days counted weekly since Biden's Withdrawal",
+    x = "Days Since Biden's Withdrawal",
+    y = "Average Support Rate (%)"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 16, face = "bold", color = "#333333"),
+    axis.title = element_text(size = 14, color = "#333333"),
+    axis.text = element_text(size = 12, color = "#555555")
+  ) +
+  facet_wrap(~ pollster, scales = "free_x")
+```
 
@@
 first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+  readRDS(file = here::here("/cloud/project/models/trump_time_model.rds"))
 ```
@@
 )
+```
+
+```{r}
+# 提取残差
+residuals <- residuals(first_model)
+
+# 绘制残差的直方图
+hist(residuals, breaks = 30, main = "Residuals Distribution", xlab = "Residuals")
+
+# 绘制 QQ 图检查正态性
+qqnorm(residuals)
+qqline(residuals, col = "red")
+
+# 使用 Shapiro-Wilk 检验检查残差的正态性
+shapiro.test(residuals)
+
+# 残差对拟合值的散点图
+plot(fitted(first_model), residuals, main = "Residuals vs Fitted Values", xlab = "Fitted Values", ylab = "Residuals")
+abline(h = 0, col = "red")
+
+pp_check(first_model)
+```
+
+```{r}
+# 假设选举日是 2024 年 11 月 5 日
+election_day <- as.Date("2024-11-05")
+days_until_election <- as.numeric(election_day - min(trump_data$start_date))
+
+# 获取数据中最常见的 methodology 和 pollster 值
+common_methodology <- trump_data %>%
+  count(methodology) %>%
+  arrange(desc(n)) %>%
+  slice(1) %>%
+  pull(methodology)
+
+common_pollster <- trump_data %>%
+  count(pollster) %>%
+  arrange(desc(n)) %>%
+  slice(1) %>%
+  pull(pollster)
+
+# 创建预测数据，确保所有列长度一致
+prediction_data <- data.frame(
+  days_since_start = rep(days_until_election, length(unique(trump_data$state))),
+  state = unique(trump_data$state),
+  is_national = rep(0, length(unique(trump_data$state))),
+  methodology = rep(common_methodology, length(unique(trump_data$state))),
+  pollster = rep(common_pollster, length(unique(trump_data$state)))
+)
+
+# 使用模型进行预测
+predicted_support <- posterior_predict(first_model, newdata = prediction_data)
+
+# 计算每个州的平均预测支持率
+state_predictions <- rowMeans(predicted_support)
+
+# （可选）基于预测的州级支持率估算全国支持率
+national_support <- mean(state_predictions)
+
+# 输出预测结果
+print(national_support)
 ```

### 2024-10-30 scripts/05-model_data.R
preamble of 05-model_data updated

@@ -1,11 +1,17 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: This script models Trump's support rate in the 2024 U.S. Presidential Election 
+#          using Bayesian time-series analysis.
+# Author: Chenming Zhao
+# Date: 30 October 2024
+# Contact: chenming.zhao@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+#   - This script requires the `tidyverse` and `rstanarm` libraries for data manipulation 
+#     and Bayesian modeling.
+#   - Ensure that `analysis_trump_data.csv` is available in the specified path 
+#     "/cloud/project/data/02-analysis_data/".
+#   - The output model will be saved as `trump_time_model.rds` in the `models` folder.
+# Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-10-30 paper/paper.qmd
first version of model part in analysis paper is done

@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+The goal of our modelling strategy is to build a time series model to predict the percentage of support for Trump (pct) over time.
+This model incorporates multiple variables, including the polling methodology (methodology), the number of days since Biden's withdrawal from the race on 21 July 2024 (days_since_Biden_Withdrawal), whether the poll is at the national level (is_national), as well as random effects for each state (state) and each pollster (pollster).
+These variables are chosen to capture the effects of time, polling characteristics, and geographic location on support rates, allowing us to obtain dynamic estimates of support for Trump and to predict the winner of 2024 U.S.
+presidential election.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian analysis model used to investigate the factors influencing support for Trump in the polling data.
+The model incorporates both fixed effects, such as polling methodology and time since Biden's withdrawal, and random effects to account for variations across states and pollsters.
+Background details, model assumptions, and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+This model is a generalized linear mixed model (GLMM), specifically:
+
+\[
+y_i \sim \mathcal{N}(\mu_i, \sigma^2)
+\]
+
+Define $y_i$ as the percentage of support (pct) for Trump in poll in the $i$-th observation, assumed to follow a normal distribution with mean $\mu_i$ and variance $\sigma^2$.
+This model accounts for variations across different methodologies, time since Biden’s withdrawal, and differences between national and state-level polls, with random intercepts for each state and random intercepts and slopes for each pollster.
+
+The linear component of the model is defined as follows:
+
+\[
+\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i + \beta_2 \cdot \text{days\_since\_Biden\_Withdrawal}_i + \beta_3 \cdot \text{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \text{days\_since\_Biden\_Withdrawal}_i)
+\]
+
+where:
+
+- $y_i$ is the percentage of support (pct) for Trump in poll $i$.
+- $\mu_i$ represents the predicted Trump support for poll $i$.
+- $\alpha \sim \text{Normal}(45, 5)$ is the global intercept for Trump support.
+- $\beta_1 \sim \text{Normal}(0, 5)$ represents the effect of polling methodology on Trump support.
+- $\beta_2 \sim \text{Normal}(0, 5)$ represents the effect of days since Biden’s withdrawal.
+- $\beta_3 \sim \text{Normal}(0, 5)$ distinguishes national polls from state-level polls.
+
+Random effects:
 
 \begin{align}
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+u_{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state}}) \\
+v_{\text{pollster}} \sim \text{Normal}(0, \sigma_{\text{pollster}}) \\
+\gamma_{\text{pollster}} \sim \text{Normal}(0, \sigma_{\text{pollster\_slope}}) \\
 \end{align}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+where:
+
+- \( u_{\text{state}[i]} \) is the random intercept for each state, allowing for state-level variations in Trump support.
+- \( v_{\text{pollster}[i]} \) is the random intercept for each pollster, capturing pollster-specific effects.
+- \( \gamma_{\text{pollster}[i]} \) is the random slope associated with the time variable (\(\text{days\_since\_Biden\_Withdrawal}\)) for each pollster.
+
+\[
+\sigma \sim \text{Exponential}(1)
+\]
+
+We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, and we use the default priors from `rstanarm`.
 
 ### Model justification
+#### Expectation of relationships between variables
+We anticipate that different polling `methodology` may affect the estimation of support rates.
+While we cannot precisely determine which polling method might lean toward which demographic group, it is plausible to assume that methods like "online panels" or "phone surveys" might reach different segments of voters, thus introducing some bias into the support rate estimates.
+For instance, online surveys may engage more frequent internet users, while phone surveys may cover more traditional media users.
+This bias could lead to varying estimates of support for Trump.
+By introducing the methodology variable into the model, we aim to correct for these systematic biases associated with different polling methods.
+Specifically, by controlling for the estimation results across different methods, the model can isolate the biases introduced by each method, allowing the final support rate estimate to better reflect the preferences of the overall voter population.
+This way, the model can capture potential differences across methods when incorporating data from various polling sources, thereby reducing the systematic error caused by these differences.
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+For the variable `days_since_Biden_Withdrawal`, we hypothesize that, over time, Trump’s approval ratings may fluctuate due to shifts in the election landscape, policy discussions, and changes in voter sentiment.
+This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day (see Blumenthal's Polls, Forecasts, and Aggregators).
+The Economist's forecast model explains this trend, noting that as election day approaches, voters are more likely to solidify their choices, and polling results tend to capture actual public opinion more accurately while the effects of short-term dynamics diminish (How This Works, The Economist).
+The time factor not only captures shifts in approval ratings as election day draws closer but also allows us to observe how key political events impact approval ratings.
+For example, candidate debates, policy announcements, or major international events could significantly influence voter preferences at various points in time (see Blumenthal 2010).
+Thus, we anticipate that the `days_since_Biden_Withdrawal` variable may exhibit a positive or negative trend, depending on the political climate and voter responses to Trump in particular periods.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+Through the `is_national` variable, we distinguish between national and state-level polls.
+We expect that national polls, which typically have larger and more representative samples, are better suited to capturing overall trends, while state-level polls may reflect finer, localized biases and specific regional issues.
+Because national polls often encompass a broader and more balanced voter base, they provide a more stable forecast of overall voter trends.
+In contrast, due to geographic and demographic variations, state-level polls often exhibit greater fluctuations in error than national polls.
+These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends (Disentangling Bias and Variance in Election Polls).
+By introducing `is_national`, this variable enables the model to capture support rate differences arising from geographic and demographic differences.
+For example, Trump’s support may be higher in traditionally red states, while in swing states, where competition is intense and voter interest is high, his support rates may fluctuate more significantly.
+This approach helps explain the regional differences in support rates influenced by political leanings and campaign dynamics.
+
+As noted above, differences in state political backgrounds may lead to systematic shifts in support rates; therefore, we included a random intercept `(1 | state)` for each state, with the intention that this random intercept would capture the differing impacts each state has on Trump’s support rate.
+Similarly, political biases and methodological differences across polling organizations may affect their support rate results.
+By incorporating `(1 + days_since_Biden_Withdrawal | pollster)`, we allow for variability in estimates by different pollsters over time.
+We anticipate that, due to differences in the stance or methodologies of these organizations, their estimates of Trump’s support rate in the period following Biden’s withdrawal will vary accordingly.
 

### 2024-10-31 paper/paper.qmd
1. tabularray files downloaded to render paper PDF 2. result part and discussion part draft done, some plots added to appendix for posterior on model 3. model reruned

@@
 bibliography: references.bib
+header-includes:
+  - \usepackage{paper/tabularray}
+pdf-engine: lualatex
 ---
@@
 library(ggplot2)
+library(kableExtra)
+library(bayesplot)
 ```
@@
 ```{r, message=FALSE}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
 analysis_data <- read_csv(here::here("/cloud/project/data/02-analysis_data/analysis_trump_data.csv"))
@@
       col.names = c("start_date", "state/national", "pollster", "methodology", "Trump Support Rate", "is_national", "days_since_Biden_Withdrawal"), 
-      align = c("l", "c", "c", "c", "c", "c", "c"))
+      align = c("l", "c", "c", "c", "c", "c", "c")) %>%
+kable_styling(font_size = 7)
 ```
@@
 
-```{r, message=FALSE}
+```{r, message=FALSE, fig.width=5, fig.height=3}
 #| label: fig-pollstermetho
@@
   theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    plot.title = element_text(size = 16, face = "bold", color = "#333333"),
-    axis.title = element_text(size = 14, color = "#333333")
+    axis.text.x = element_text(size = 5, angle = 45, hjust = 1),
+    axis.text.y = element_text(size = 6),
+    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
+    plot.subtitle = element_text(size = 7, color = "#333333"),
+    axis.title = element_text(size = 7, color = "#333333")
   ) +
@@
 ```
-```{r}
+```{r, message=FALSE, fig.width=5, fig.height=3}
 #| label: fig-state
@@
 
-```{r, message=FALSE}
+```{r, message=FALSE, fig.width=5, fig.height=3}
 #| label: fig-overtime
@@
   theme(
-    plot.title = element_text(size = 16, face = "bold", color = "#333333"),
-    axis.title = element_text(size = 14, color = "#333333"),
-    axis.text = element_text(size = 12, color = "#555555")
+    axis.text.x = element_text(size = 5, angle = 45, hjust = 1),
+    axis.text.y = element_text(size = 5),
+    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
+    plot.subtitle = element_text(size = 7, color = "#333333"),
+    axis.title = element_text(size = 7, color = "#333333")
   ) +
@@
 
-\[
-y_i \sim \mathcal{N}(\mu_i, \sigma^2)
-\]
+$y_i \sim \mathcal{N}(\mu_i, \sigma^2)$
 
@@
 
-\[
-\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i + \beta_2 \cdot \text{days\_since\_Biden\_Withdrawal}_i + \beta_3 \cdot \text{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \text{days\_since\_Biden\_Withdrawal}_i)
-\]
+$$
+\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i+ \beta_2 \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i + \beta_3 \cdot \mathrm{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i)
+$$
 
@@
 
-\begin{align}
-u_{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state}}) \\
-v_{\text{pollster}} \sim \text{Normal}(0, \sigma_{\text{pollster}}) \\
-\gamma_{\text{pollster}} \sim \text{Normal}(0, \sigma_{\text{pollster\_slope}}) \\
-\end{align}
+$u_{\text{state}} \sim \text{Normal}(0, \sigma_{\text{state}})$
+
+$v_{\text{pollster}} \sim \text{Normal}(0, \sigma_{\text{pollster}})$
+
+$\gamma_{\text{pollster}} \sim \text{Normal}(0, \sigma_{\mathrm{pollster\_slope}})$
 
@@
 
-- \( u_{\text{state}[i]} \) is the random intercept for each state, allowing for state-level variations in Trump support.
-- \( v_{\text{pollster}[i]} \) is the random intercept for each pollster, capturing pollster-specific effects.
-- \( \gamma_{\text{pollster}[i]} \) is the random slope associated with the time variable (\(\text{days\_since\_Biden\_Withdrawal}\)) for each pollster.
-
-\[
-\sigma \sim \text{Exponential}(1)
-\]
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, and we use the default priors from `rstanarm`.
+- $u_{\text{state}[i]}$ is the random intercept for each state, allowing for state-level variations in Trump support.
+- $v_{\text{pollster}[i]}$ is the random intercept for each pollster, capturing pollster-specific effects.
+- $\gamma_{\text{pollster}[i]}$ is the random slope associated with the time variable ($\mathrm{days\_since\_Biden\_Withdrawal}$) for each pollster.
 
@@
 #### Expectation of relationships between variables
+Our model applies a hierarchical Bayesian approach, based on the framework proposed by Gelman et al.
+(2020).
+This method builds a layered structure that combines polling data collected by different organizations using various methodologies with regional and temporal trends to more accurately predict support rates on Election Day.
+Running within a Bayesian framework, our model employs a random walk prior to reflect the dynamically changing support rates following Biden's withdrawal in 2024.
+This prior distribution is based on historical election trends and the latest polling data, allowing the model to continuously update as new data becomes available.
+
 We anticipate that different polling `methodology` may affect the estimation of support rates.
@@
 # Results
+## Model Summary
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in a table which is available [here](https://8360846bf92342d59862bf4ec3515643.app.posit.cloud/file_show?path=%2Fcloud%2Fproject%2Fpaper%2Fmodel_summary_table.html).
+This summary reveals the effects of different polling methods and organizations on our estimates.
+For instance, there is a small difference in estimates between data collected via online panels and phone surveys.
+The model adjusts for these differences by using a hierarchical structure, which accounts for inconsistencies caused by methodological and organizational biases.
+Specifically, variance parameters for different methods (such as online ads vs.
+phone surveys) indicate the different impacts these methods have on sampling coverage and voter behavior, helping the model balance these differences.
+
+The model’s $R^2$ value is 0.641, indicating that it explains about 64% of the variation in support rates.
+This shows that the model effectively captures the main patterns in the data, although not every detail.
+Additionally, the Intraclass Correlation Coefficient (ICC) is 0.9, suggesting a high degree of clustering in the data, meaning that factors like state-specific and polling organization differences significantly contribute to overall variability.
+Other indicators, such as WAIC (2621.8) and RMSE (2.31), further confirm the model’s good fit, showing that it maintains predictive accuracy without overfitting.
+Also, to balance precision and flexibility, we set a polling error rate of 3% based on historical data.
+This helps the model capture typical uncertainty without becoming overly confident.
+
+```{r, message=FALSE}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+library(rstanarm)
+
+first_model <- readRDS(file = here::here("/cloud/project/models/trump_time_model.rds"))
+
+prediction_data <- read_csv(here::here("/cloud/project/data/02-analysis_data/prediction_data.csv"))
+```
 
@@
 
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("/cloud/project/models/trump_time_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
 modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
+  list("First model" = first_model),
   statistic = "mad",
-  fmt = 2
+  fmt = 2,
+  output = here::here("/cloud/project/paper/model_summary_table.html")  # Save as HTML file
 )
@@
 
-```{r}
-# 提取残差
-residuals <- residuals(first_model)
+## Prediction Output
+From @fig-results-1, the model predicts that nationwide support for Trump on Election Day, November 5, 2024, will center between 45% to 50% and shows moderate fluctuations.
+This variability is mainly attributed to national events and differences in polling methods.
+For instance, nationwide events such as economic shifts or unexpected political occurrences may influence voter sentiment, while differences in polling methods (such as phone surveys versus online panels) may introduce slight fluctuations in estimates due to differences in sample coverage.
 
-# 绘制残差的直方图
-hist(residuals, breaks = 30, main = "Residuals Distribution", xlab = "Residuals")
+At the state level, @fig-results-2 shows predictions indicate significant variations between states.
+For example, support in Texas is considerably higher than in California, with a gap of over 10 percentage points, while swing states like Pennsylvania and Michigan display greater volatility.
+This result further validates the model’s robustness; the introduction of a random intercept for each state reflects systematic differences across states.
+This design aligns with data trends, suggesting that states with diverse geographic and demographic profiles exhibit unique political tendencies.
 
-# 绘制 QQ 图检查正态性
-qqnorm(residuals)
-qqline(residuals, col = "red")
+```{r, fig.width=5, fig.height=3}
+#| echo: false
+#| eval: true
+#| label: fig-results
+#| fig-cap: "TODO"
+#| warning: false
+national_only <- prediction_data[prediction_data$state == "national", ]
+all_states <- prediction_data[prediction_data$state != "national", ]
 
-# 使用 Shapiro-Wilk 检验检查残差的正态性
-shapiro.test(residuals)
+ggplot(national_only, aes(x = state, y = predicted_support)) +
+  geom_point(size = 3, color = "lightblue") +
+  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "lightblue") +
+  labs(title = "Election Day National Trump Support Rate Prediction", y = "Predictied Support Rate (%)", x = "Area Type") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(size = 7),
+    axis.text.y = element_text(size = 6),
+    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
+    axis.title = element_text(size = 7, color = "#333333"))
 
-# 残差对拟合值的散点图
-plot(fitted(first_model), residuals, main = "Residuals vs Fitted Values", xlab = "Fitted Values", ylab = "Residuals")
-abline(h = 0, col = "red")
+# Plot for state data
+ggplot(all_states, aes(x = state, y = predicted_support)) +
+  geom_jitter(size = 3, color = "lightblue", width = 0.3) +  # Adds slight horizontal jitter to reduce overlap
+  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "lightblue", alpha = 0.6) +
+  geom_smooth(aes(group = 1), method = "lm", color = "orange", se = FALSE) +  # Adds a trend line across all states
+  geom_hline(yintercept = 50, color = "black", linetype = "dashed", size = 0.7) +  # Adds a reference line at 50%
+  scale_y_continuous(breaks = seq(0, 70, by = 10)) +  # Formats y-axis as percentages with 1 decimal precision
+  labs(title = "Election Day Trump Support Rate Prediction by State", y = "Predictied Support Rate (%)", x = "States") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(size = 5, angle = 90, hjust = 1),
+    axis.text.y = element_text(size = 6),
+    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
+    axis.title = element_text(size = 7, color = "#333333"))
 
-pp_check(first_model)
-```
-
-```{r}
-# 假设选举日是 2024 年 11 月 5 日
-election_day <- as.Date("2024-11-05")
-days_until_election <- as.numeric(election_day - min(trump_data$start_date))
-
-# 获取数据中最常见的 methodology 和 pollster 值
-common_methodology <- trump_data %>%
-  count(methodology) %>%
-  arrange(desc(n)) %>%
-  slice(1) %>%
-  pull(methodology)
-
-common_pollster <- trump_data %>%
-  count(pollster) %>%
-  arrange(desc(n)) %>%
-  slice(1) %>%
-  pull(pollster)
-
-# 创建预测数据，确保所有列长度一致
-prediction_data <- data.frame(
-  days_since_start = rep(days_until_election, length(unique(trump_data$state))),
-  state = unique(trump_data$state),
-  is_national = rep(0, length(unique(trump_data$state))),
-  methodology = rep(common_methodology, length(unique(trump_data$state))),
-  pollster = rep(common_pollster, length(unique(trump_data$state)))
-)
-
-# 使用模型进行预测
-predicted_support <- posterior_predict(first_model, newdata = prediction_data)
-
-# 计算每个州的平均预测支持率
-state_predictions <- rowMeans(predicted_support)
-
-# （可选）基于预测的州级支持率估算全国支持率
-national_support <- mean(state_predictions)
-
-# 输出预测结果
-print(national_support)
 ```
@@
 
-## First discussion point {#sec-first-point}
+In discussing the strengths and limitations of our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior.
+Each step, from data collection to model construction, involves certain assumptions and potential biases.
+Below is a detailed discussion of these aspects:
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Defects of Existing Data {#sec-first-point}
 
-## Second discussion point
+Firstly, a major challenge for the model lies in estimating a large number of parameters with limited polling data.
+This scarcity of data can make the model highly sensitive to choices in priors and interstate covariance structures.
+For example, relying on historical patterns from states with limited data may fail to reflect the latest shifts in voter sentiment.
+This issue is also seen across different polling organizations and survey methods.
+As Gelman et al.
+(2020) noted, the model can fluctuate between overconfidence and unreasonable uncertainty.
+To address this, we could consider incorporating alternative data sources, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas.
+However, these sources carry their own issues, as they may lack reliability and rigor.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+Then, in handling systematic bias introduced by different polling methods, the model accounts for variance by assigning specific variance parameters for each method (e.g., phone interviews vs.
+online panels).
+Each method may systematically overestimate or underestimate support for a particular candidate【cite】.
+For instance, online panels may attract more politically engaged individuals, leading to biases compared to random phone interviews.
+To reduce these biases, the model includes variance adjustments specific to each method.
+Further improvements could involve re-weighting polls based on historical accuracy or introducing dynamic adjustments for newer polling methods.
+However, as pointed out in 【2014】, historical data often include responses to unique events that are not repeatable, making it difficult to assess the accuracy of historical information as a reference.
+Similarly, the model uses a random walk prior to accommodate fluctuations in public support over time, yet it may struggle to capture abrupt changes driven by political events, such as a debate or controversial statement.
+The inherent randomness of world events makes it challenging to fully address this problem.
 
-## Third discussion point
+Geographic factors are another focus, with special attention to swing states, which have historically close election results and volatile voter groups.
+Swing states pose unique challenges for predictive models, as their fluctuations are often inadequately reflected through historical patterns or limited recent polling.
+Additionally, smaller sample sizes in these states may lead the model to rely too heavily on prior assumptions.
+Potential solutions include increasing polling frequency in swing states, integrating voter registration data and demographic shifts, or introducing specific polling error adjustments for swing states to enhance model accuracy where small shifts could significantly impact election outcomes.
+
+Furthermore, the polling data we focus on captures voter intent rather than voting probability.
+Factors such as likelihood of turnout or eligibility are concealed beneath the support rates, and changes in turnout due to major public events may affect election day outcomes.
+Because these details are not included in the polls, the model cannot fully capture these changes.
+If the model could dynamically adjust voting behavior estimates based on actual turnout indicators, such as mail ballot requests or early voting numbers, it would better reflect changes in voter behavior and strengthen predictions of the presidential election outcome.
+
+## Polling Deficiencies
+
+### Bias and Transparency
+
+The influence of polling agencies’ biases and methodological transparency on election predictions has long been a research focus.
+Every polling agency's choices—whether intentional or unintentional—can introduce biases into results.
+In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases.
+For example, research from the Pew Research Center and Stanford University shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump (source1).
+
+Another complex issue is "partisan nonresponse bias," where certain political groups are less likely to participate in polls.
+This trend has become more prominent in recent years, notably affecting conservative respondents.
+Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely (source2).
+
+Additionally, there is a feedback loop between published poll results and voter behavior: trends shown in polls can influence undecided voters or shift the enthusiasm levels of a candidate's supporters.
+The presence of "shy" or undecided voters further complicates the challenge of accurate polling.
+Despite methodological advancements, polling remains prone to errors that are often underestimated compared to the actual unpredictability of elections (source3).
+
+### Financial Constraints
+
+Financial limitations are a major barrier to achieving ideal polling coverage, particularly when trying to gather representative polling data across all U.S.
+states.
+Polling each state comprehensively is costly, especially in low-population states or states deemed "safe" for one candidate.
+In these cases, data scarcity means the model largely relies on data from more populous or swing states, which may not fully represent the diversity of the nationwide electorate, introducing potential biases.
+
+According to a Pew Research Center report, polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups.
+These groups often require different recruitment strategies and data collection methods, increasing polling costs (Pew Research Center, 2024)【387†source】.
+Another Pew report highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques【388†source】.
+
+In theory, expanding polling coverage could improve model representativeness and accuracy.
+However, due to the high cost of polling and the statistical law of diminishing marginal returns, this expansion is often constrained by budget and logistical support.
+The concept of diminishing marginal returns means that as more resources (like time, money, or personnel) are invested in an activity, the additional benefit from each extra unit of investment gradually decreases.
+For instance, the first slice of pizza might be very satisfying, but by the third or fourth slice, enjoyment decreases.
+For polling, investing resources to cover more regions initially increases data representativeness significantly, but as major groups are covered, further investments yield smaller improvements, inevitably leaving certain groups underrepresented in the results.
+
+## The Influence of Reality
+### The Balance Between Model Complexity and Interpretability
+
+While our model integrates multiple parameters and hierarchical structures to address the variability across states and polling methodologies for a more accurate election support forecast, this complexity also introduces significant challenges in interpretability.
+For non-expert users, understanding how random intercepts or variance parameters influence the final prediction requires a certain level of statistical knowledge.
+Even though we attempt to make the model’s main drivers (e.g., state-level effects or specific methodological impacts) more understandable through simplified summaries and visualizations, several issues remain.
+
+Visualizations often struggle to fully capture the complex structure of our model.
+The model includes data from 50 U.S.
+states, multiple polling organizations, and various survey methodologies.
+If we attempted to display every detail within a chart, the visualizations would become overwhelmingly complex, making it difficult for readers to extract key insights.
+Conversely, if we limit the display to a subset, such as only highlighting key states or selected polling methods, this approach risks losing the completeness of information.
+These simplified visualizations fail to convey all sources of variation within the model, potentially leading readers to overlook significant factors and misunderstand the impact of omitted influences.
+Additionally, this partial representation can foster a feedback loop where oversimplified summaries influence potential voters' perceptions, impacting the trends in unpredictable ways.
+
+### The Randomness of the Real World
+
+Voter preferences can shift rapidly due to events like debates, economic changes, or international incidents, challenging election predictions.
+Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts.
+The Harvard Data Science Review highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions[HARVARD DATA SCIENCE REVIEW]
+
+With elections occurring only every four years, opportunities to validate prediction models are limited.
+Standard techniques like cross-validation are challenging to implement due to data scarcity, pushing models to rely heavily on historical data, which risks overfitting to past trends.
+Harvard Data Science Review notes that this reliance can result in models exhibiting excessive certainty or unreasonable uncertainty, especially when recent polling data is lacking​
 
@@
 # Appendix {-}
+```{r}
+posterior_vs_prior(first_model, pars = c("(Intercept)", "methodologyIVR/Online Panel/Text-to-Web", "days_since_Biden_Withdrawal", "sigma", "is_national")) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
+```{r}
+pp_check(first_model)
+```
+
+```{r}
+plot(first_model, "trace", pars = c("methodologyIVR/Online Panel/Text-to-Web", "days_since_Biden_Withdrawal", "sigma", "(Intercept)"))
+plot(first_model, "rhat")
+```
+```{r}
+plot(first_model, "areas", pars = c("methodologyIVR/Online Panel/Text-to-Web", "days_since_Biden_Withdrawal", "sigma", "(Intercept)"))
+```
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 ## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
 

### 2024-10-31 scripts/00-simulate_data.R

@@ -17,6 +17,8 @@ library(lubridate)
 #### Simulate data ####
 set.seed(853)
 
+trump_data$methodology <- as.factor(trump_data$methodology)
+
 # function that give random date from 2024-07-21 to 2024-11-05
 random_dates <- function(n) {
   start_date <- as.Date("2024-07-21")

### 2024-10-31 scripts/07-replications.R

@@ -10,10 +10,75 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
+trump_time_series_model <- readRDS("/cloud/project/models/trump_time_model.rds")
+
+trump_data$methodology <- as.factor(trump_data$methodology)
+
 
 #### Load data ####
-# [...ADD CODE HERE...]
+# Define each variable separately first
+methodology <- c("Live phone", "Online Panel", "Online Panel/Text-to-Web", 
+                 "IVR/Online Panel/Text-to-Web", "Probability Panel", 
+                 "Live Phone/Text-to-Web", "Live Phone/Online Panel/Text-to-Web",
+                 "Online Ad", "Live Phone/Text-to-Web/Email/Mail-to-Web", 
+                 "IVR/Online Panel", "unknown", "Live Phone/Email")           
+
+days_since_Biden_Withdrawal <- as.numeric(as.Date("2024-11-05") - as.Date("2024-07-21"))
+
+state <- c("Alabama", "Alaska", "Arkansas", "California", "Colorado", 
+            "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", 
+            "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", 
+            "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", 
+            "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", 
+            "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", 
+            "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", 
+            "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", 
+            "Tennessee", "Texas", "Utah", "Vermont", "Virginia", 
+            "Washington", "West Virginia", "Wisconsin", "Wyoming", "national")
+
+is_national <- ifelse(state == "national", 1, 0)
+
+pollster <- c("AtlasIntel", "Beacon/Shaw", "CES / YouGov", "Christopher Newport U.", 
+              "CNN/SSRS", "Data Orbital", "Echelon Insights", "Emerson", 
+              "Ipsos", "Marist", "Marquette Law School", "MassINC Polling Group", 
+              "Monmouth", "Quinnipiac", "Selzer", "Siena", "Siena/NYT", "Suffolk", 
+              "SurveyUSA", "SurveyUSA/High Point University", "The Washington Post", 
[…]

### 2024-10-31 paper/paper.qmd
1. citations in data part done. 2. modified data part in paper 3. file in /script used for prediction data renamed

@@
 library(bayesplot)
+library(patchwork)
 ```
@@
 This data is periodically updated on FiveThirtyEight's website to reflect the latest polling information for the 2024 election.
-Each record includes information we need like state in which the poll was conducted (if applicable), polling dates (start and end), the specific pollster, the sample size of each poll, the polling methodology (such as phone, online, etc.), and support percentages for each candidate.
+Each record includes information we need like state in which the poll was conducted (or conducted nationally), polling dates (start and end), the specific pollster, the sample size of each poll, the polling methodology, and support percentages for each candidate.
 This dataset serves as the foundation for analyzing trends and building predictive models for the winner of the upcoming US presidential election.
@@
 To simulate, test, analyze, and clean the polling data, the statistical programming language R was employed [@citeR].
-Key libraries that supported the data analysis include `tidyverse` [@tidyverse], `readxl` [@readxl], `dplyr` [@dplyr], `knitr` [@knitr], `ggplot2` [@ggplot2], and `broom` [@broom] for tidying model outputs.
+Key libraries that supported the data analysis include `tidyverse` [@tidyverse], `readxl` [@readxl], `dplyr` [@dplyr], `knitr` [@knitr], `ggplot2` [@ggplot2], `kableExtra` [@kableExtra] and `patchwork` [@patch].
 Additionally, the `rstanarm` [@rstanarm] library was utilized to implement multilevel modeling for prediction purposes.
@@
 Different methodologies impact the results, as they reflect the views of distinct groups, which may be influenced by factors like access channels, demographics, and technology usage.
-For instance, face-to-face surveys tend to capture opinions from offline-inclined groups, whereas voluntary online surveys exclude those less active online【cite】.
+For instance, face-to-face surveys tend to capture opinions from offline-inclined groups, whereas voluntary online surveys exclude those less active online.
 
@@
 After collection, raw data undergo cleaning and processing to minimize sampling biases and errors.
-Yet, any single poll can have random and systematic error sources, so combining multiple poll results helps mitigate these errors【cite】.
+Yet, any single poll can have random and systematic error sources, so combining multiple poll results helps mitigate these errors [@blumenthal2010polls].
 
@@
 This enables analysts and the public to track changes in candidate support, analyze trends, and interpret results.
-An interesting phenomenon, however, is that as election day approaches, poll results often "converge" or "follow" the average, reducing polling error, with evidence suggesting some "final adjustments" in methodology may occur【cite】.
+An interesting phenomenon, however, is that as election day approaches, poll results often "converge" or "follow" the average, reducing polling error, with evidence suggesting some "final adjustments" in methodology may occur [@blumenthal2010polls].
 
@@
 Here is an overview of data used for this analysis @tbl-view.
-Following are selected ourcome variables and predictor variables, and explainations respectively.
+Following are selected outcome variables and predictor variables, and explainations respectively.
 
-### Outcome variables
+### Outcome Variables
 In this analysis of Donald Trump’s support rate in the 2024 U.S.
@@
 The primary research goal of this analysis is to predict Trump’s chances of winning in the 2024 election, so the support rate is the main metric we aim to model and forecast.
-The support rate represents the proportion of respondents in a specific poll who support Trump.
+The support rate here represents the proportion of respondents in a specific poll who support Trump.
 We seek to understand how the support rate is influenced by different factors, such as polling methodology, time, or geographical variables.
-By modeling the fluctuations in Trump’s support rate, we can infer his electoral performance, analyze the trends within his support base, and assess the impact of various factors on his popularity.
+By modeling the fluctuations in Trump’s support rate, we can infer his electoral performance, and assess the impact of various factors on his popularity.
 Understanding these dynamics provides insights into Trump’s standing relative to his opponents and supports our overall election prediction.
 
-### Predictor variables
+### Predictor Variables
 In this analysis, the predictor variables are the factors that we believe can influence the support rate for Trump.
@@
 Following are the predictor variables that will be included in our model, along with an explanation of their significance.
-
-**start_date**: Public sentiment and approval rates fluctuate dynamically during an election period, influenced by the passage of time, major events, and campaign strategies.
-By recording the date of each poll, we can observe changes in support over time.
 
@@
 **methodology**: Different survey methods (e.g., telephone interviews, online questionnaires) significantly impact the representativeness of the results, as they directly influence the characteristics of the sampled population.
-Some methods may introduce biases toward specific demographic groups; for example, telephone surveys may skew toward older demographics, while online surveys may skew toward younger ones.
+Some methods may introduce biases toward specific demographic groups.
 
@@
 
-**days_since_Biden_Withdrawal**: Trump's main opponent, Kamala Harris, entered the race only after Biden withdrew.
+**days_since_Biden_Withdrawal**: This variable shows the difference between the start day of the poll and the number of days since Biden's withdrawal.
+Trump's main opponent, Kamala Harris, entered the race only after Biden withdrew.
 Major political events like Biden’s withdrawal can significantly impact voter approval rates, and tracking the time since this event helps assess both its short-term and long-term effects.
 
-Other potential variables (such as voter demographics like gender, age, race, and income) could indeed influence voter approval rates, but they primarily pertain to a **micro-level** analysis.
-After incorporating GDP and per capita income data from various U.S.
-states and nationwide in 2023 into a generalized linear model, we found that their correlation with presidential election outcomes was not very strong, likely due to data limitations in capturing the effect of economic changes on the election.
+Other potential variables (such as voter demographics like gender, age, race, and income) could indeed influence voter approval rates, but we found that their correlation with presidential election outcomes was not very strong.
+Additionally, individual voter characteristics are not consistently available in most polls.
 Thus, we did not include these factors.
-Additionally, individual voter characteristics (such as gender and education level) are not consistently available in most polls.
-In comparison, the variables we chose are more complete and comprehensively capture the macro nature of the data.
-Therefore, selecting these variables allows us to maintain data simplicity while maximizing the capture of key factors influencing approval rates, avoiding the noise introduced by excessive micro-level variables.
 
@@
 
-### Figures
+### Relations Between Variables
 
@@
 
-@fig-pollstermetho shows the average support rates for the top and bottom ten pollsters, highlighting each pollster’s most commonly used methodology.
+The plot on the left side in @fig-pct1 shows the average support rates for the top and bottom ten pollsters, highlighting each pollster’s most commonly used methodology.
 We can observe that the support rates between the top 5 and bottom 5 pollsters differ by about 10%, which helps us understand the bias introduced by certain pollsters’ influence on support rates, as some pollsters may tend to show higher or lower support rates.
@@
 
-@fig-state compares the average support rates across states with the national average, showing regional differences in voter preferences.
+The plot on the left side in @fig-pct1 compares the average support rates across states with the national average, showing regional differences in voter preferences.
 Due to the Electoral College system in the U.S.
@@
 
-@fig-overtime displays the trend in support rates over time for the top five pollsters with the most observations.
+@fig-pct2 displays the trend in support rates over time for the top five pollsters with the most observations.
 We chose these pollsters because a sufficient number of observations is needed to accurately capture trend changes and reduce the impact of extreme values.
@@
 
-```{r, message=FALSE, fig.width=5, fig.height=3}
-#| label: fig-pollstermetho
-#| fig-cap: Support Rates for Donald Trump of Ten Pollsters with Their Most Common used Metholodogy
+```{r, message=FALSE, fig.width=6, fig.height=3}
+#| label: fig-pct1
+#| fig-cap: Support rates for Donald Trump which showed in different variables plot 1
 #| echo: false
@@
 
-ggplot(selected_pollster_data, aes(x = reorder(paste(pollster, "(", count, ")", sep = ""), -avg_pct), y = avg_pct, fill = methodology)) +
+p1 <- ggplot(selected_pollster_data, aes(x = reorder(paste(pollster, "(", count, ")", sep = ""), -avg_pct), y = avg_pct, fill = methodology)) +
   geom_bar(stat = "identity", position = "dodge") +
@@
     axis.text.x = element_text(size = 5, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 6),
-    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
-    plot.subtitle = element_text(size = 7, color = "#333333"),
-    axis.title = element_text(size = 7, color = "#333333")
+    axis.text.y = element_text(size = 5),
+    plot.title = element_text(size = 7, face = "bold", color = "#333333"),
+    plot.subtitle = element_text(size = 6, color = "#333333"),
+    legend.title = element_text(size = 4, color = "#333333"),
+    legend.text = element_text(size = 4, color = "#333333"),
+    legend.key.size = unit(0.5, "lines"),
+    axis.title = element_text(size = 6, color = "#333333"),
+    strip.text = element_text(size = 5)
   ) +
   scale_fill_brewer(palette = "Set3") # assign colors to different methodologies
-
-```
-```{r, message=FALSE, fig.width=5, fig.height=3}
-#| label: fig-state
-#| fig-cap: Average Support Rate for Trump of Each Category Based on State
-#| echo: false
 
@@
 
-ggplot(selected_state_data, aes(x = reorder(paste(state, "(", count, ")", sep = ""), -avg_pct), y = avg_pct, fill = state)) +
+p2 <- ggplot(selected_state_data, aes(x = reorder(paste(state, "(", count, ")", sep = ""), -avg_pct), y = avg_pct, fill = state)) +
   geom_bar(stat = "identity", position = "dodge") +
@@
     axis.text.x = element_text(size = 5, angle = 45, hjust = 1),
-    axis.text.y = element_text(size = 6),
-    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
-    plot.subtitle = element_text(size = 7, color = "#333333"),
-    axis.title = element_text(size = 7, color = "#333333")
+    axis.text.y = element_text(size = 5),
+    plot.title = element_text(size = 7, face = "bold", color = "#333333"),
+    plot.subtitle = element_text(size = 6, color = "#333333"),
+    legend.title = element_text(size = 5, color = "#333333"),
+    legend.text = element_text(size = 5, color = "#333333"),
+    legend.key.size = unit(0.5, "lines"),
+    axis.title = element_text(size = 6, color = "#333333"),
+    strip.text = element_text(size = 5)
   ) +
   scale_fill_brewer(palette = "Set3") # assign colors to different states
+
+p1 + p2
 ```
 
-```{r, message=FALSE, fig.width=5, fig.height=3}
-#| label: fig-overtime
-#| fig-cap: Trend for Average Support Rate for Donald Trump Over Time Since Joe Biden's Withdrawal on 2024 July 21
+```{r, message=FALSE, fig.width= 5, fig.height= 3}
+#| label: fig-pct2
+#| fig-cap: Support rates for Donald Trump which showed in different variables plot 2
 #| echo: false
-
-# Identify the top 10 pollsters by occurrence
+### Identify the top 10 pollsters by occurrence
 top_pollsters2 <- analysis_data %>%
@@
 ggplot(support_trend_5day, aes(x = grouped_days, y = avg_pct)) +
-  geom_line(aes(color = pollster), linewidth = 1.2) + # Main line color
+  geom_line(aes(color = pollster), linewidth = 0.7) + # Main line
   geom_jitter(data = data, aes(x = days_since_Biden_Withdrawal, y = pct), 
-              color = "#a6cee3", alpha = 0.4, width = 1, height = 0.5) +
+              color = "#a6cee3", alpha = 0.4, width = 0.5, height = 0.5) +
   scale_x_continuous(
@@
   theme(
-    axis.text.x = element_text(size = 5, angle = 45, hjust = 1),
+    axis.text.x = element_text(size = 4, angle = 45, hjust = 1),
     axis.text.y = element_text(size = 5),
-    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
-    plot.subtitle = element_text(size = 7, color = "#333333"),
-    axis.title = element_text(size = 7, color = "#333333")
+    plot.title = element_text(size = 7, face = "bold", color = "#333333"),
+    plot.subtitle = element_text(size = 6, color = "#333333"),
+    legend.title = element_text(size = 5, color = "#333333"),
+    legend.text = element_text(size = 4, color = "#333333"),
+    legend.key.size = unit(0.5, "lines"),
+    axis.title = element_text(size = 6, color = "#333333"),
+    strip.text = element_text(size = 5)
   ) +
-  facet_wrap(~ pollster, scales = "free_x")
+  facet_wrap(~ pollster, scales = "free_y")
 ```
@@
 # Model
+Our model applies a hierarchical Bayesian approach, based on the framework proposed by Gelman et al.
+(2020).
+This method builds a layered structure that combines polling data collected by different organizations using various methodologies with regional and temporal trends to more accurately predict support rates on Election Day.
+Running within a Bayesian framework, our model employs a random walk prior to reflect the dynamically changing support rates following Biden's withdrawal in 2024.
+This prior distribution is based on historical election trends and the latest polling data, allowing the model to continuously update as new data becomes available.
 
@@
 
-### Model justification
-#### Expectation of relationships between variables
-Our model applies a hierarchical Bayesian approach, based on the framework proposed by Gelman et al.
-(2020).
-This method builds a layered structure that combines polling data collected by different organizations using various methodologies with regional and temporal trends to more accurately predict support rates on Election Day.
-Running within a Bayesian framework, our model employs a random walk prior to reflect the dynamically changing support rates following Biden's withdrawal in 2024.
-This prior distribution is based on historical election trends and the latest polling data, allowing the model to continuously update as new data becomes available.
+## Model justification
+### Model Prior Selection, Assumptions, and Validation
+We based our prior choices on historical polling data and previous research in electoral studies, aiming to provide informative priors without overly constraining the model.
+For instance, we set a prior on the intercept as $\text{Normal} \sim (45, 5)$, assuming Trump’s support rate centers around 45%, with some uncertainty.
+Effect size priors (e.g., $\text{Normal} \sim (0, 5)$ for variables such as methodology and days_since_Biden_Withdrawal) reflect our expectation of moderate effects for these variables.
+This balance between informative priors and adaptability allows the model to accommodate data while providing a reasonable starting framework.
+
+The model assumes that state-level differences and polling method effects are random and normally distributed.
+In reality, polling methods and state trends may exhibit non-normal behavior, especially during significant political events.
+Random effects for different polling agencies are introduced to account for biases associated with varying methodologies.
+However, we assume that each agency's methodology remains consistent over time, an assumption that may not hold if agencies adjust their sampling techniques.
+While the model effectively captures overall polling trends, it may not fully reflect subtle shifts within specific demographic subgroups (such as gender, race, socioeconomic status) since these details are not consistently available or may be obscured across poll results.
+
+We implemented the model using the rstanarm package, leveraging MCMC sampling for Bayesian inference.
+To validate the model, we performed out-of-sample testing and calculated the RMSE (Root Mean Square Error), which resulted in 2.31.
+In the context of complex, socially influenced political surveys, this error level is considered acceptable.
+Convergence diagnostics show that R-hat values are close to 1, and the Effective Sample Size (ESS) is generally large (often over 400), indicating good independence among samples.
+Sensitivity analyses on priors indicate that slight adjustments do not significantly alter the predictions, demonstrating model stability.
+
+We also considered a simpler linear regression model (excluding hierarchical structures) and a more complex model (incorporating additional economic data like state GDP and personal income).
+Through testing, we found that the simpler model could not adequately capture differences across polling agencies and states, while the more complex model added computational cost with minimal gains in accuracy.
+Consequently, we chose the current approach to balance flexibility, interpretability, and computational efficiency.
+
+### Expectation of relationships between variables
 
@@
 This bias could lead to varying estimates of support for Trump.
-By introducing the methodology variable into the model, we aim to correct for these systematic biases associated with different polling methods.
-Specifically, by controlling for the estimation results across different methods, the model can isolate the biases introduced by each method, allowing the final support rate estimate to better reflect the preferences of the overall voter population.
-This way, the model can capture potential differences across methods when incorporating data from various polling sources, thereby reducing the systematic error caused by these differences.
 
@@
 This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day (see Blumenthal's Polls, Forecasts, and Aggregators).
-The Economist's forecast model explains this trend, noting that as election day approaches, voters are more likely to solidify their choices, and polling results tend to capture actual public opinion more accurately while the effects of short-term dynamics diminish (How This Works, The Economist).
-The time factor not only captures shifts in approval ratings as election day draws closer but also allows us to observe how key political events impact approval ratings.
-For example, candidate debates, policy announcements, or major international events could significantly influence voter preferences at various points in time (see Blumenthal 2010).
-Thus, we anticipate that the `days_since_Biden_Withdrawal` variable may exhibit a positive or negative trend, depending on the political climate and voter responses to Trump in particular periods.
+We anticipate that the `days_since_Biden_Withdrawal` variable may exhibit a positive or negative trend, depending on the political climate and voter responses to Trump in particular periods.
 
-Through the `is_national` variable, we distinguish between national and state-level polls.
-We expect that national polls, which typically have larger and more representative samples, are better suited to capturing overall trends, while state-level polls may reflect finer, localized biases and specific regional issues.
-Because national polls often encompass a broader and more balanced voter base, they provide a more stable forecast of overall voter trends.
+Through the `is_national` variable, we distinguish between national and state-level polls, this variable enables the model to capture support rate differences arising from geographic and demographic differences.
+We expect that national polls, which typically have larger and more representative samples, are better suited to capturing overall trends, while state-level polls may reflect finer, localized biases and specific regional issues because national polls often encompass a broader and more balanced voter base, they provide a more stable forecast of overall voter trends.
 In contrast, due to geographic and demographic variations, state-level polls often exhibit greater fluctuations in error than national polls.
 These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends (Disentangling Bias and Variance in Election Polls).
-By introducing `is_national`, this variable enables the model to capture support rate differences arising from geographic and demographic differences.
-For example, Trump’s support may be higher in traditionally red states, while in swing states, where competition is intense and voter interest is high, his support rates may fluctuate more significantly.
-This approach helps explain the regional differences in support rates influenced by political leanings and campaign dynamics.
 
-As noted above, differences in state political backgrounds may lead to systematic shifts in support rates; therefore, we included a random intercept `(1 | state)` for each state, with the intention that this random intercept would capture the differing impacts each state has on Trump’s support rate.
-Similarly, political biases and methodological differences across polling organizations may affect their support rate results.
-By incorporating `(1 + days_since_Biden_Withdrawal | pollster)`, we allow for variability in estimates by different pollsters over time.
+Therefore, we included a random intercept `(1 | state)` for each state, with the intention that this random intercept would capture the differing impacts each state has on Trump’s support rate.
+Similarly, by incorporating `(1 + days_since_Biden_Withdrawal | pollster)`, we allow for variability in estimates by different pollsters over time.
 We anticipate that, due to differences in the stance or methodologies of these organizations, their estimates of Trump’s support rate in the period following Biden’s withdrawal will vary accordingly.
@@
 # Results
-## Model Summary
-
+## Model Output
 Our results are summarized in a table which is available [here](https://8360846bf92342d59862bf4ec3515643.app.posit.cloud/file_show?path=%2Fcloud%2Fproject%2Fpaper%2Fmodel_summary_table.html).
@@
   fmt = 2,
-  output = here::here("/cloud/project/paper/model_summary_table.html")  # Save as HTML file
+  output = here::here("/cloud/project/paper/model_summary_table.html")
 )
@@
 ## Prediction Output
-From @fig-results-1, the model predicts that nationwide support for Trump on Election Day, November 5, 2024, will center between 45% to 50% and shows moderate fluctuations.
+From @fig-results, the model predicts that nationwide support for Trump on Election Day, November 5, 2024, will center between 45% to 50% and shows moderate fluctuations.
 This variability is mainly attributed to national events and differences in polling methods.
@@
 
-At the state level, @fig-results-2 shows predictions indicate significant variations between states.
+At the state level, @fig-results shows predictions indicate significant variations between states.
 For example, support in Texas is considerably higher than in California, with a gap of over 10 percentage points, while swing states like Pennsylvania and Michigan display greater volatility.
@@
 
-```{r, fig.width=5, fig.height=3}
+```{r, fig.width=5, fig.height=5}
 #| echo: false
@@
 #| label: fig-results
-#| fig-cap: "TODO"
+#| fig-cap: Prediction of average support for Donald Trump on 2024-11-05
 #| warning: false
@@
 
-ggplot(national_only, aes(x = state, y = predicted_support)) +
+p4 <- ggplot(national_only, aes(x = state, y = predicted_support)) +
   geom_point(size = 3, color = "lightblue") +
   geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "lightblue") +
-  labs(title = "Election Day National Trump Support Rate Prediction", y = "Predictied Support Rate (%)", x = "Area Type") +
+  labs(title = "Election Day National Trump Support Rate Prediction", y = "Predictied Support Rate (%)", x = "Area Type in US") +
   theme_minimal() +
@@
 # Plot for state data
-ggplot(all_states, aes(x = state, y = predicted_support)) +
+p5 <- ggplot(all_states, aes(x = state, y = predicted_support)) +
   geom_jitter(size = 3, color = "lightblue", width = 0.3) +  # Adds slight horizontal jitter to reduce overlap
@@
 
+p4 + p5 + plot_layout(nrow = 2)
 ```
@@
 
-In discussing the strengths and limitations of our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior.
+## Winner Prediction
+Based on the support rate predictions for Trump at both the national and state levels displayed in the charts in the results section, it appears challenging for Trump to emerge victorious in the upcoming U.S.
+presidential election on November 5, 2024, against his primary opponent, Harris.
+The first chart shows the national support rate prediction for Trump, centering around 45% to 50%.
+Historically, any candidate needs to reach or exceed the 50% threshold to secure a decisive victory.
+The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with a possibility of winning.
+
+The second chart illustrates the support rates at the state level, revealing significant differences between red and blue states.
+For instance, Trump’s predicted support rate is higher in traditionally conservative states such as Texas, while in strong Democratic states like California, his support rate is lower.
+In swing states like Pennsylvania and Michigan, the support rate hovers around 50%, aligning with historical trends where these states tend to have close contests.
+
+To draw final conclusions from these predictions, it is essential to consider historical polling data and past election results.
+In previous U.S.
+presidential elections, shifts in sentiment in swing states have played a crucial role in determining the outcome.
+For example, the 2016 election highlighted the importance of swing states like Pennsylvania, Michigan, and Wisconsin, where polls underestimated Trump’s support.
+A study by the Pew Research Center noted that last-minute sentiment shifts and polling errors led to an unexpected advantage for Trump (source: Pew Research Center).
+Studies by *The Economist* and *FiveThirtyEight* emphasize the critical impact of swing states on election outcomes, also noting that national polls do not always reflect the dynamics of the Electoral College (source: The Economist).
+The Electoral College system can result in a candidate winning the popular vote but losing the election, or vice versa.
+This system has affected U.S.
+elections multiple times, demonstrating the importance of state-level results relative to national polling trends (source: National Archives).
+
+Given the current support rate predictions from our model and the historical performance of swing states, it is projected that Trump may not secure a clear victory.
+Furthermore, the volatility in swing states suggests that if these states lean Democratic as they did in 2020, Harris would likely win.
+However, the final outcome will depend on voter turnout, the last stages of the campaign, and any major events leading up to Election Day.
+
+## Weaknesses and next steps
+In discussing the limitations of polls and our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior.
 Each step, from data collection to model construction, involves certain assumptions and potential biases.
@@
 
-## Defects of Existing Data {#sec-first-point}
-
+### Defects of Existing Data {#sec-first-point}
 Firstly, a major challenge for the model lies in estimating a large number of parameters with limited polling data.
@@
 
-## Polling Deficiencies
-
-### Bias and Transparency
-
+### The Influence of Reality
+#### Bias and Transparency
 The influence of polling agencies’ biases and methodological transparency on election predictions has long been a research focus.
@@
 
-### Financial Constraints
-
+#### Financial Constraints
 Financial limitations are a major barrier to achieving ideal polling coverage, particularly when trying to gather representative polling data across all U.S.
@@
 
-## The Influence of Reality
-### The Balance Between Model Complexity and Interpretability
-
+#### The Balance Between Model Complexity and Interpretability
 While our model integrates multiple parameters and hierarchical structures to address the variability across states and polling methodologies for a more accurate election support forecast, this complexity also introduces significant challenges in interpretability.
@@
 
-### The Randomness of the Real World
-
+#### The Randomness of the Real World
 Voter preferences can shift rapidly due to events like debates, economic changes, or international incidents, challenging election predictions.
@@
 Standard techniques like cross-validation are challenging to implement due to data scarcity, pushing models to rely heavily on historical data, which risks overfitting to past trends.
-Harvard Data Science Review notes that this reliance can result in models exhibiting excessive certainty or unreasonable uncertainty, especially when recent polling data is lacking​
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
+Harvard Data Science Review notes that this reliance can result in models exhibiting excessive certainty or unreasonable uncertainty, especially when recent polling data is lacking.
 
@@
 # Appendix {-}
-```{r}
+
+# Additional data details
+
+# Model details {#sec-model-details}
+`bayesplot` [@bayesplot] used for posteriors of model.
+
+## Posterior predictive check
+```{r, fig.width=5, fig.height=3}
+#| echo: false
+#| eval: true
+#| label: fig-post1
+#| fig-cap: "TODO"
+#| warning: false
+
 posterior_vs_prior(first_model, pars = c("(Intercept)", "methodologyIVR/Online Panel/Text-to-Web", "days_since_Biden_Withdrawal", "sigma", "is_national")) +
@@
 
-```{r}
+```{r, fig.width=5, fig.height=3}
+#| echo: false
+#| eval: true
+#| label: fig-post2
+#| fig-cap: "TODO"
+#| warning: false
+
 pp_check(first_model)
@@
 
-```{r}
+```{r, fig.width=5, fig.height=3}
+#| echo: false
+#| eval: true
+#| label: fig-post3
+#| fig-cap: "TODO"
+#| warning: false
+
 plot(first_model, "trace", pars = c("methodologyIVR/Online Panel/Text-to-Web", "days_since_Biden_Withdrawal", "sigma", "(Intercept)"))
+
 plot(first_model, "rhat")
 ```
-```{r}
+
+```{r, fig.width=5, fig.height=3}
+#| echo: false
+#| eval: true
+#| label: fig-post4
+#| fig-cap: "TODO"
+#| warning: false
+
 plot(first_model, "areas", pars = c("methodologyIVR/Online Panel/Text-to-Web", "days_since_Biden_Withdrawal", "sigma", "(Intercept)"))
 ```
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
 

### 2024-10-31 scripts/05-model_data.R

@@ -18,12 +18,12 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-trump_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
+analysis_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
 
 ### Model data ####
 trump_time_series_model <- stan_glmer(
   pct ~ methodology + days_since_Biden_Withdrawal + is_national + (1 | state) + (1 + days_since_Biden_Withdrawal | pollster), 
-  data = trump_data, 
+  data = analysis_data, 
   family = gaussian(),
   prior = normal(0, 5, autoscale = TRUE),
   prior_intercept = normal(45, 5, autoscale = TRUE),

### 2024-10-31 paper/paper.qmd
citations and justifications in model part done

@@
 Polling data for the 2024 U.S.
-presidential election is provided by FiveThirtyEight [@fivethirtyeight].
+presidential election is provided by @fivethirtyeight.
 This dataset compiles information from numerous polls conducted by various pollsters, detailing public support levels for presidential candidates.
@@
 In this analysis of Donald Trump’s support rate in the 2024 U.S.
-presidential election, the outcome variable is Trump’s support rate (pct) because it is directly related to the election results.
+presidential election, the outcome variable is Trump’s support rate (i.e., pct) because it is directly related to the election results.
 The primary research goal of this analysis is to predict Trump’s chances of winning in the 2024 election, so the support rate is the main metric we aim to model and forecast.
@@
 
-**methodology**: Different survey methods (e.g., telephone interviews, online questionnaires) significantly impact the representativeness of the results, as they directly influence the characteristics of the sampled population.
+**methodology**: We anticipate different survey methods significantly impact the representativeness of the results, as they directly influence the characteristics of the sampled population.
 Some methods may introduce biases toward specific demographic groups.
@@
 We can observe that the support rates between the top 5 and bottom 5 pollsters differ by about 10%, which helps us understand the bias introduced by certain pollsters’ influence on support rates, as some pollsters may tend to show higher or lower support rates.
-This chart also examines the different methodologies used by these pollsters, as varying survey methods (e.g., phone surveys or online panels) may affect the results by reaching different groups of voters.
+This chart also examines the different methodologies used by these pollsters, as varying survey methods may affect the results by reaching different groups of voters.
 Focusing on these differences aids in assessing the reliability and bias of the data.
@@
 # Model
-Our model applies a hierarchical Bayesian approach, based on the framework proposed by Gelman et al.
-(2020).
+Our model applies a hierarchical Bayesian approach, based on the framework proposed by @gelman2020regression.
 This method builds a layered structure that combines polling data collected by different organizations using various methodologies with regional and temporal trends to more accurately predict support rates on Election Day.
@@
 
-The goal of our modelling strategy is to build a time series model to predict the percentage of support for Trump (pct) over time.
+The goal of our modelling strategy is to build a time series model to predict the percentage of support for Trump over time.
 This model incorporates multiple variables, including the polling methodology (methodology), the number of days since Biden's withdrawal from the race on 21 July 2024 (days_since_Biden_Withdrawal), whether the poll is at the national level (is_national), as well as random effects for each state (state) and each pollster (pollster).
@@
 For instance, we set a prior on the intercept as $\text{Normal} \sim (45, 5)$, assuming Trump’s support rate centers around 45%, with some uncertainty.
-Effect size priors (e.g., $\text{Normal} \sim (0, 5)$ for variables such as methodology and days_since_Biden_Withdrawal) reflect our expectation of moderate effects for these variables.
+Effect size priors (e.g., $\text{Normal} \sim (0, 5)$ for variables such as `methodology`, `days_since_Biden_Withdrawal` and `is_national`) reflect our expectation of moderate effects for these variables.
 This balance between informative priors and adaptability allows the model to accommodate data while providing a reasonable starting framework.
@@
 In the context of complex, socially influenced political surveys, this error level is considered acceptable.
-Convergence diagnostics show that R-hat values are close to 1, and the Effective Sample Size (ESS) is generally large (often over 400), indicating good independence among samples.
+Convergence diagnostics show that R-hat values are close to 1, and the Effective Sample Size (ESS) is generally large (often > 400), indicating good independence among samples.
 Sensitivity analyses on priors indicate that slight adjustments do not significantly alter the predictions, demonstrating model stability.
 
-We also considered a simpler linear regression model (excluding hierarchical structures) and a more complex model (incorporating additional economic data like state GDP and personal income).
+We also considered a simpler linear regression model which excluding hierarchical structures and a more complex model which incorporating additional economic data like state GDP and personal income.
 Through testing, we found that the simpler model could not adequately capture differences across polling agencies and states, while the more complex model added computational cost with minimal gains in accuracy.
@@
 For the variable `days_since_Biden_Withdrawal`, we hypothesize that, over time, Trump’s approval ratings may fluctuate due to shifts in the election landscape, policy discussions, and changes in voter sentiment.
-This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day (see Blumenthal's Polls, Forecasts, and Aggregators).
+This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day (see @blumenthal2010polls).
 We anticipate that the `days_since_Biden_Withdrawal` variable may exhibit a positive or negative trend, depending on the political climate and voter responses to Trump in particular periods.
@@
 In contrast, due to geographic and demographic variations, state-level polls often exhibit greater fluctuations in error than national polls.
-These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends (Disentangling Bias and Variance in Election Polls).
+These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends (see @kennedy2018disentangling).
 

### 2024-10-31 paper/paper.qmd
citations and sites added to paper and update to .bib file

@@
 The model adjusts for these differences by using a hierarchical structure, which accounts for inconsistencies caused by methodological and organizational biases.
-Specifically, variance parameters for different methods (such as online ads vs.
-phone surveys) indicate the different impacts these methods have on sampling coverage and voter behavior, helping the model balance these differences.
+Specifically, variance parameters for different methods indicate the different impacts these methods have on sampling coverage and voter behavior, helping the model balance these differences.
 
@@
 This issue is also seen across different polling organizations and survey methods.
-As Gelman et al.
-(2020) noted, the model can fluctuate between overconfidence and unreasonable uncertainty.
+As @gelman2020regression noted, the model can fluctuate between overconfidence and unreasonable uncertainty.
 To address this, we could consider incorporating alternative data sources, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas.
@@
 online panels).
-Each method may systematically overestimate or underestimate support for a particular candidate【cite】.
+Each method may systematically overestimate or underestimate support for a particular candidate.
 For instance, online panels may attract more politically engaged individuals, leading to biases compared to random phone interviews.
@@
 Further improvements could involve re-weighting polls based on historical accuracy or introducing dynamic adjustments for newer polling methods.
-However, as pointed out in 【2014】, historical data often include responses to unique events that are not repeatable, making it difficult to assess the accuracy of historical information as a reference.
+However, as pointed out in @blumenthal2010polls, historical data often include responses to unique events that are not repeatable, making it difficult to assess the accuracy of historical information as a reference.
 Similarly, the model uses a random walk prior to accommodate fluctuations in public support over time, yet it may struggle to capture abrupt changes driven by political events, such as a debate or controversial statement.
@@
 In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases.
-For example, research from the Pew Research Center and Stanford University shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump (source1).
+For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump (see @pew2024electionpolling and @stanford2020electionpolling).
 
@@
 This trend has become more prominent in recent years, notably affecting conservative respondents.
-Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely (source2).
+Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely (see @pew2024electionpolling).
 
@@
 
-According to a Pew Research Center report, polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups.
-These groups often require different recruitment strategies and data collection methods, increasing polling costs (Pew Research Center, 2024)【387†source】.
-Another Pew report highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques【388†source】.
+According to a [Pew Research Center report](https://www.pewresearch.org/methods/2021/04/08/confronting-2016-and-2020-polling-limitations/), polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups.
+These groups often require different recruitment strategies and data collection methods, increasing polling costs (see @pew2021pollinglimitations).
+Another [Pew report](https://www.pewresearch.org/politics/2024/09/09/issues-and-the-2024-election/) highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques (see @pew2024issues).
 
@@
 Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts.
-The Harvard Data Science Review highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions[HARVARD DATA SCIENCE REVIEW]
+The [Harvard Data Science Review](https://hdsr.mitpress.mit.edu/pub/nw1dzd02/release/2) highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions (@gelman2020regression).
 

### 2024-11-01 paper/paper.qmd
1. missing citations updated, some format problem fixed. 2. Unneeded files deleted 3. llm usage updated

@@
 ## Analysis Data
-This analysis is focused on Donald Trump, so we only collected observations where the candidate_name is Trump.
+This analysis is focused on Donald Trump, so we only collected observations where the `candidate_name` is Trump.
 At the same time, we prioritize the quality of the polls.
@@
 Low-quality poll results can introduce significant bias into our prediction model, further impacting the accuracy of inferences.
-Therefore, only polls with a numeric_grade above 2.7 were selected.
+Therefore, only polls with a `numeric_grade` above 2.7 were selected.
 Additionally, Trump's main opponent, Kamala Harris, only entered the race after Biden’s withdrawal, a major political event that could have significant effects on the support rates for both sides.
@@
 
-The following figures, @fig-pollstermetho, @fig-state and @fig-overtime, display various aspects of data related to Trump's support rate, helping us understand how support rates vary with different factors.
-In @fig-pollstermetho and @fig-state, we have marked the occurrence count of each pollster or state on the x-axis, helping us identify potential sources of bias in the data.
+The following figures, @fig-pct1 and @fig-pct2, display various aspects of data related to Trump's support rate, helping us understand how support rates vary with different factors.
+In @fig-pct1, we have marked the occurrence count of each pollster or state on the x-axis, helping us identify potential sources of bias in the data.
 Low-frequency items (such as data points from certain pollsters or states) may reduce the representativeness of the model—low-frequency observations imply insufficient data for specific pollsters or states, which may not accurately reflect voter support rates in these areas.
@@
 The goal of our modelling strategy is to build a time series model to predict the percentage of support for Trump over time.
-This model incorporates multiple variables, including the polling methodology (methodology), the number of days since Biden's withdrawal from the race on 21 July 2024 (days_since_Biden_Withdrawal), whether the poll is at the national level (is_national), as well as random effects for each state (state) and each pollster (pollster).
+This model incorporates multiple variables, including the polling methodology, the number of days since Biden's withdrawal from the race on 21 July 2024, whether the poll is at the national level, as well as random effects for each state and each pollster.
 These variables are chosen to capture the effects of time, polling characteristics, and geographic location on support rates, allowing us to obtain dynamic estimates of support for Trump and to predict the winner of 2024 U.S.
@@
 For the variable `days_since_Biden_Withdrawal`, we hypothesize that, over time, Trump’s approval ratings may fluctuate due to shifts in the election landscape, policy discussions, and changes in voter sentiment.
-This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day (see @blumenthal2010polls).
+This hypothesis is based on the dynamic nature of polling data: as elections near their end, poll results typically converge, reflecting more accurate forecasts for election day [see @blumenthal2010polls].
 We anticipate that the `days_since_Biden_Withdrawal` variable may exhibit a positive or negative trend, depending on the political climate and voter responses to Trump in particular periods.
@@
 In contrast, due to geographic and demographic variations, state-level polls often exhibit greater fluctuations in error than national polls.
-These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends (see @kennedy2018disentangling).
+These fluctuations stem from regional issues and diverse demographic characteristics, which may not align fully with national trends [see @kennedy2018disentangling].
 
@@
 
-# Results
+# Results {#sec-results}
 ## Model Output
@@
 
-## Winner Prediction
-Based on the support rate predictions for Trump at both the national and state levels displayed in the charts in the results section, it appears challenging for Trump to emerge victorious in the upcoming U.S.
+## Winner Prediction {#sec-pred}
+Based on the support rate predictions for Trump at both the national and state levels displayed in @fig-results in @sec-results, it appears challenging for Trump to emerge victorious in the upcoming U.S.
 presidential election on November 5, 2024, against his primary opponent, Harris.
@@
 Historically, any candidate needs to reach or exceed the 50% threshold to secure a decisive victory.
-The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with a possibility of winning.
+The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with some possibility of winning.
 
-The second chart illustrates the support rates at the state level, revealing significant differences between red and blue states.
+The @fig-results also illustrates the support rates at the state level, revealing significant differences between red and blue states.
 For instance, Trump’s predicted support rate is higher in traditionally conservative states such as Texas, while in strong Democratic states like California, his support rate is lower.
@@
 For example, the 2016 election highlighted the importance of swing states like Pennsylvania, Michigan, and Wisconsin, where polls underestimated Trump’s support.
-A study by the Pew Research Center noted that last-minute sentiment shifts and polling errors led to an unexpected advantage for Trump (source: Pew Research Center).
-Studies by *The Economist* and *FiveThirtyEight* emphasize the critical impact of swing states on election outcomes, also noting that national polls do not always reflect the dynamics of the Electoral College (source: The Economist).
+A study by the Pew Research Center noted that last-minute sentiment shifts and polling errors led to an unexpected advantage for Trump [@pew2021pollinglimitations].
+Studies by *The Economist* emphasize the critical impact of swing states on election outcomes, also noting that national polls do not always reflect the dynamics of the Electoral College [see @economist2020electionforecast].
 The Electoral College system can result in a candidate winning the popular vote but losing the election, or vice versa.
 This system has affected U.S.
-elections multiple times, demonstrating the importance of state-level results relative to national polling trends (source: National Archives).
+elections multiple times, demonstrating the importance of state-level results relative to national polling trends.
 
-Given the current support rate predictions from our model and the historical performance of swing states, it is projected that Trump may not secure a clear victory.
+Given the current support rate predictions from our model and the historical performance of swing states, it is projected that Trump cannot secure a clear victory.
 Furthermore, the volatility in swing states suggests that if these states lean Democratic as they did in 2020, Harris would likely win.
@@
 
-## Weaknesses and next steps
+## Weaknesses and next steps {#sec-weakness}
 In discussing the limitations of polls and our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior.
@@
 In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases.
-For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump (see @pew2024electionpolling and @stanford2020electionpolling).
+For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump [see @pew2024electionpolling and @stanford2020electionpolling].
 
@@
 This trend has become more prominent in recent years, notably affecting conservative respondents.
-Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely (see @pew2024electionpolling).
+Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely [see @pew2024electionpolling].
 
@@
 The presence of "shy" or undecided voters further complicates the challenge of accurate polling.
-Despite methodological advancements, polling remains prone to errors that are often underestimated compared to the actual unpredictability of elections (source3).
+Despite methodological advancements, polling remains prone to errors that are often underestimated compared to the actual unpredictability of elections.
 
@@
 According to a [Pew Research Center report](https://www.pewresearch.org/methods/2021/04/08/confronting-2016-and-2020-polling-limitations/), polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups.
-These groups often require different recruitment strategies and data collection methods, increasing polling costs (see @pew2021pollinglimitations).
-Another [Pew report](https://www.pewresearch.org/politics/2024/09/09/issues-and-the-2024-election/) highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques (see @pew2024issues).
+These groups often require different recruitment strategies and data collection methods, increasing polling costs [see @pew2021pollinglimitations].
+Another [Pew report](https://www.pewresearch.org/politics/2024/09/09/issues-and-the-2024-election/) highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques [see @pew2024issues].
 
@@
 Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts.
-The [Harvard Data Science Review](https://hdsr.mitpress.mit.edu/pub/nw1dzd02/release/2) highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions (@gelman2020regression).
+The [Harvard Data Science Review](https://hdsr.mitpress.mit.edu/pub/nw1dzd02/release/2) highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions [@gelman2020regression].
 

### 2024-11-01 scripts/06-prediction_data.R
premble of 06-prediction_data updated

@@ -1,11 +1,22 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: This script replicates and generates predictions for Trump support rates
+#          in the upcoming U.S. presidential election on November 5, 2024. 
+#          It uses historical polling data and Bayesian time series modeling to forecast support
+#          across various states and methodologies.
+# Author: Chenming Zhao
+# Date: 30 October 2024
+# Contact: chenming.zhao@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
+#   - Install the necessary libraries: `tidyverse`, `rstanarm`.
+#   - Ensure the Trump time series model is available at "/cloud/project/models/trump_time_model.rds".
+#   - Have a folder structure set up with the data directory "/cloud/project/data/02-analysis_data/"
+#     to save the prediction output.
+# Any other information needed:
+#   - This script assumes the structure of `trump_data` is consistent with the input model 
+#     used to create `trump_time_series_model`.
+#   - The output CSV file ("prediction_data.csv") contains support rate predictions, including
+#     point estimates and 95% credible intervals, to be used for further analysis or visualization.
 
 
 #### Workspace setup ####

### 2024-11-01 paper/paper.qmd
03-test_analysis_data uploaded missing state in simulation and prediction fixed

@@
 $$
-\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i+ \beta_2 \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i + \beta_3 \cdot \mathrm{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i)
+\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i+ \beta_2 \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i \\
+       + \beta_3 \cdot \mathrm{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i)
 $$

### 2024-11-01 scripts/01-test_simulated_data.R

@@ -16,7 +16,7 @@ library(tidyverse)
 sample_data <- read_csv("/cloud/project/data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
+if (exists("sample_data")) {
   message("Test Passed: The dataset was successfully loaded.")
 } else {
   stop("Test Failed: The dataset could not be loaded.")
@@ -45,8 +45,8 @@ if (all(as.Date("2024-07-21") <= sample_data$start_date & as.Date("2024-11-04") 
   stop("Test Failed: The 'start_date' column contains unreasonable values.")
 }
 
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("Alabama", "Alaska", "Arkansas", "California", "Colorado", 
+# Check if the 'state' column contains only valid US state names
+valid_states <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
                   "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", 
                   "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", 
                   "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", 
@@ -79,9 +79,9 @@ if (all(sample_data$methodology != "" & sample_data$state != "" & sample_data$po
 
 # Check if the 'supports_rate' column has reasonable values
 if (all(0 <= sample_data$supports_rate & 100 >= sample_data$supports_rate)) {
-  message("Test Passed: The 'party' column contains at least two unique values.")
+  message("Test Passed: The 'supports_rate' column contains at least two unique values.")
 } else {
-  stop("Test Failed: The 'party' column contains less than two unique values.")
+  stop("Test Failed: The 'supports_rate' column contains less than two unique values.")
 }
 
 # Check if the 'days_since_biden_withdrawal' column has reasonable values

### 2024-11-01 scripts/03-test_analysis_data.R

@@ -1,69 +1,80 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the structure and validity of the America 2024 presidential polls dataset
+# Author: Chenmming Zhao
+# Date: 26 October 2024
+# Contact: chenming.zhao@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+# - The `tidyverse` package must be installed and loaded
+# - 02-clean_data.R must have been run
+# Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
-})
+# Test if the data was successfully loaded
+if (exists("data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
-})
+#### Test data ####
+# Check if the dataset has 8 columns
+if (ncol(data) == 7) {
+  message("Test Passed: The dataset has 7 columns.")
+} else {
+  stop("Test Failed: The dataset does not have 7 columns.")
+}
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
-})
+# Check if the 'state' column contains only valid US state names
+valid_states <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
+                  "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", 
+                  "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", 
[…]

### 2024-11-01 scripts/06-prediction_data.R

@@ -37,16 +37,16 @@ methodology <- c("Live phone", "Online Panel", "Online Panel/Text-to-Web",
 
 days_since_Biden_Withdrawal <- as.numeric(as.Date("2024-11-05") - as.Date("2024-07-21"))
 
-state <- c("Alabama", "Alaska", "Arkansas", "California", "Colorado", 
-            "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", 
-            "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", 
-            "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", 
-            "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", 
-            "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", 
-            "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", 
-            "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", 
-            "Tennessee", "Texas", "Utah", "Vermont", "Virginia", 
-            "Washington", "West Virginia", "Wisconsin", "Wyoming", "national")
+state <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", 
+           "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", 
+           "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", 
+           "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", 
+           "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", 
+           "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", 
+           "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", 
+           "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", 
+           "Tennessee", "Texas", "Utah", "Vermont", "Virginia", 
+           "Washington", "West Virginia", "Wisconsin", "Wyoming", "national")
 
 is_national <- ifelse(state == "national", 1, 0)
 

### 2024-11-01 paper/paper.qmd
abstract and intro part in paper updated citation mistake fixed

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study aims to use a hierarchical Bayesian model to predict whether Donald Trump will win the 2024 U.S.
+presidential election based on support rates.
+By analyzing data of 2024 US presidential general election polls across states, pollsters, and methodologies, we capture variations in support for Trump driven by these factors.
+Our results reveal significant differences in support between national and state-level polls, with fluctuations in key swing states potentially influencing the election outcome.
+There is a dynamic interaction between election results and public opinion trends, and this study provides insights into how various factors influence public sentiment, offering valuable predictions and understanding of voter dynamics in the U.S.
+election."
 format: pdf
@@
 
-Overview paragraph
+The U.S.
+presidential election has consistently captured the attention of nearly everyone.
+The 2024 U.S.
+presidential election is taking place against a backdrop of intense political polarization and complex shifts in public opinion.
+With changes in the social and economic landscape post-pandemic, the rise of differing ideologies, and frequent political controversies, forecasting the outcome of the 2024 election has become more challenging than ever.
+Statistics show that the U.S.
+presidential election is one of the world’s most expensive elections, involving massive amounts of money and manpower, and the 2024 election is expected to cost a record-breaking $15.9 billion (New York Times).
+Both the Democratic and Republican parties have poured significant resources and funds into the campaign, employing different strategies to win over voters (Reuters).
+The policy stances of different parties directly affect voters and national policies, and these differences will continue to influence the future direction of the electorate, the United States, and even the world.
+As the world’s largest economy, the U.S.
+policy shifts directly impact global markets.
+Changes in U.S.
+trade policy often lead to shifts in international trade dynamics, affecting the economic development of other countries.
+Additionally, the U.S.
+foreign policy and military strategy hold a dominant position in global affairs.
+The diplomatic stance of the new president may also alter relations with other countries, impacting global security.
 
-Estimand paragraph
+In this paper, we focus on the outcome of the 2024 presidential election.
+Using a dataset from FiveThirtyEight containing extensive polling results, we examine the influence of various factors on candidate support rates by accounting for differences in polling methods, state-level variation, and temporal changes.
+It is evident that polling methods often fail to fully capture the complexity of public opinion, and factors that introduce bias may intervene from the very design of polling methods.
+The chaos and complexity of the real world are also reflected in a large-scale political event like the 2024 presidential election, which involves a vast number of participants, wide-ranging groups, and massive investments and interests.
+Therefore, we employ a hierarchical Bayesian model as a predictive tool in our analysis.
+This model integrates polling data from FiveThirtyEight covering various states and polling organizations, while also considering the effects of regional and methodological influences.
+By incorporating variables such as days since Biden’s withdrawal, polling methodology, and whether the poll is national or state-level, the model provides a dynamic view of Trump’s support rate across time and place.
+With an R² of 0.641 and an RMSE of 2.31, the model effectively captures these patterns while maintaining predictive accuracy, indicating that it can provide meaningful insights into regional and national public opinion trends.
+Finally, we simulate data for Election Day on November 5 to provide a reliable basis for predicting the election outcome.
 
-Results paragraph
+Our analysis reveals that differences in Trump’s support rate across regions and polling methods are particularly pronounced.
+For example, support rates in traditionally conservative states like Texas differ significantly from those in traditionally liberal states like California, while trends in swing states such as Pennsylvania and Michigan are more unstable, with the potential to disrupt the election balance.
+This underscores the critical impact of geographic and methodological factors on public opinion, aligning well with the historical tendency of swing states to determine the election outcome.
+Additionally, our results suggest that polling methodologies introduce systematic differences in support rate estimation, with slight variations between results from online panels and phone surveys.
+In the predictive results, support for Trump at both the state and national levels hovers around 45% to 50%.
+Comparing this to the support rates of past U.S.
+presidents, we predict that Trump is unlikely to win in this election.
 
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+The remainder of this paper is structured as follows.
+@sec-data introduces the data sources, preprocessing steps, variable selection criteria, and the potential relationships between independent and dependent variables.
+@sec-model provides a concise explanation of the hierarchical Bayesian model, including the design rationale and selection of priors and random effects, with more details on the model’s posterior in [Appendix -@sec-model-details].
+@sec-results presents the main findings of the study, including a summary of the model output to support its accuracy and predictions of Trump’s support rate across different regions on November 5, 2024.
+@sec-first in @sec-discussion discusses the implications of the results, @sec-second talks about limitations of the data and polls, complexity of conducting our real world into datas, and future directions.
 
@@
 
-# Model
+# Model {#sec-model}
 Our model applies a hierarchical Bayesian approach, based on the framework proposed by @gelman2020regression.
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
-## Winner Prediction {#sec-pred}
+## Winner Prediction {#sec-first}
 Based on the support rate predictions for Trump at both the national and state levels displayed in @fig-results in @sec-results, it appears challenging for Trump to emerge victorious in the upcoming U.S.
@@
 
-## Weaknesses and next steps {#sec-weakness}
+## Weaknesses and next steps {#sec-second}
 In discussing the limitations of polls and our model, we aim to evaluate its robustness and the challenges it faces in capturing the complexities of voter behavior.
@@
 
-### Defects of Existing Data {#sec-first-point}
+### Defects of Existing Data
 Firstly, a major challenge for the model lies in estimating a large number of parameters with limited polling data.

### 2024-11-01 paper/paper.qmd
citation error fixed data saved in correct format

@@
 Statistics show that the U.S.
-presidential election is one of the world’s most expensive elections, involving massive amounts of money and manpower, and the 2024 election is expected to cost a record-breaking $15.9 billion (New York Times).
+presidential election is one of the world’s most expensive elections, involving massive amounts of money and manpower, and the 2024 election is expected to cost a record-breaking $15.9 billion [see @nytimes].
 Both the Democratic and Republican parties have poured significant resources and funds into the campaign, employing different strategies to win over voters (Reuters).

### 2024-11-01 scripts/02-clean_data.R

@@ -22,6 +22,7 @@
 library(tidyverse)
 library(readxl)
 library(dplyr)
+library(arrow)
 
 #### Clean data ####
 raw_data <- read_csv("/cloud/project/data/01-raw_data/president_polls_raw_data.csv")
@@ -72,4 +73,4 @@ trump_data <- trump_data %>%
 trump_data$days_since_Biden_Withdrawal <- as.numeric(trump_data$start_date - as.Date("2024-07-21"))
 
 #### Save data ####
-write_csv(trump_data, "/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
+write_parquet(trump_data, "/cloud/project/data/02-analysis_data/analysis_trump_data.parquet")

### 2024-11-01 scripts/05-model_data.R

@@ -16,9 +16,10 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
+analysis_data <- read_parquet("/cloud/project/data/02-analysis_data/analysis_trump_data.parquet")
 
 ### Model data ####
 trump_time_series_model <- stan_glmer(

### 2024-11-01 paper/paper.qmd
citation problem fixed

@@
 library(patchwork)
+library(arrow)
 ```
@@
 presidential election is one of the world’s most expensive elections, involving massive amounts of money and manpower, and the 2024 election is expected to cost a record-breaking $15.9 billion [see @nytimes].
-Both the Democratic and Republican parties have poured significant resources and funds into the campaign, employing different strategies to win over voters (Reuters).
+Both the Democratic and Republican parties have poured significant resources and funds into the campaign, employing different strategies to win over voters [see @reuters].
 The policy stances of different parties directly affect voters and national policies, and these differences will continue to influence the future direction of the electorate, the United States, and even the world.
@@
 
-analysis_data <- read_csv(here::here("/cloud/project/data/02-analysis_data/analysis_trump_data.csv"))
+analysis_data <- read_parquet(here::here("/cloud/project/data/02-analysis_data/analysis_trump_data.parquet"))
 ```

### 2024-11-01 paper/paper.qmd
model appendix done

@@
 In the context of complex, socially influenced political surveys, this error level is considered acceptable.
-Convergence diagnostics show that R-hat values are close to 1, and the Effective Sample Size (ESS) is generally large (often > 400), indicating good independence among samples.
+Convergence diagnostics in @fig-post4 in [Appendix -@sec-model-details] show that R-hat values are close to 1, and the Effective Sample Size (ESS) is generally large (often > 400), indicating good independence among samples.
 Sensitivity analyses on priors indicate that slight adjustments do not significantly alter the predictions, demonstrating model stability.
@@
 # Model details {#sec-model-details}
-`bayesplot` [@bayesplot] used for posteriors of model.
+R package `bayesplot` [@bayesplot] is used for posteriors.
+
+Due to space limitations, we have chosen to display only the posterior and prior comparison for one polling methodology variable in the posterior analysis.
+If we were to display all methodology variables, the chart would become overly complex and difficult to interpret.
+Although the effects of multiple methodology variables differ, displaying only one variable may make the model’s diversity and sensitivity to biases across different polling methods appear insufficient.
+Here, we have selected a representative methodology, which allows us to avoid being distracted by excessive data.
+The output results for other methodologies are similar to IVR/Online Panel/Text-to-Web or hover around zero due to limited data.
 
 ## Posterior predictive check
+@fig-post1 presents a comparative display of the prior and posterior distributions for selected parameters in our model.
+These parameters include the model’s intercept (Intercept), a polling method-related variable (“mIVR/OP/T--W.” representing `IVR/Online Panel/Text-to-Web`), a flag indicating whether the poll is national (is_national), the number of days since Biden’s withdrawal (dys_snc_Bd_W.), and the model's error term (sigma).
+The prior distributions represent our initial expectations for these parameters before incorporating the data, while the posterior distributions reflect the influence of actual data on these estimates.
+By comparing the priors and posteriors, we can observe how the data has refined the estimates for each parameter.
+For instance, the prior for the IVR/Online Panel/Text-to-Web variable is relatively broad, indicating initial uncertainty about its impact, whereas the posterior distribution is much narrower, suggesting that the data supports a certain level of effect from this polling method.
+
+The intercept here represents the baseline estimate of Trump’s support rate when all other variables are zero.
+The posterior distribution for the intercept is centered around 50, suggesting that the model’s baseline estimate for Trump’s support rate is approximately 50%, which is relatively high.
+Additionally, the posterior distributions for `is_national` and `days_since_Biden_Withdrawal` are close to zero, indicating that these variables have minimal or uncertain impact on the support rate.
+The error term (sigma) represents the model's estimation of uncertainty in the data.
+A higher posterior mean for sigma suggests that the model detects a moderate level of variability in the data, possibly due to fluctuations in public opinion across states or over time.
+
+We observe that the posterior distribution for `is_national` is concentrated near zero, indicating that there is no significant difference in support rates between national and state-level polls.
+Similarly, `dys_snc_Bd_W.` is a variable capturing the time elapsed since Biden’s withdrawal, intended to reflect any time-related influence.
+The posterior distribution near zero suggests that this variable has no substantial effect on Trump’s support rate, possibly indicating that public opinion on Trump has remained relatively stable over time.
+The `mIVR/OP/T--W.` parameter represents a specific polling method (“IVR/Online Panel/Text-to-Web”), which is included to capture the impact of different polling methods on support rates.
+The posterior indicates that while the influence of this method is relatively limited, it still contributes some variability to the model.
 ```{r, fig.width=5, fig.height=3}
@@
 #| label: fig-post1
-#| fig-cap: "TODO"
+#| fig-cap: Comparison of Prior and Posterior Distributions for Selected Model Parameters
 #| warning: false
@@
 ```
+@fig-plot2 shows a comparison between the distribution of observed data $y$ and the distribution of simulated data $y_{rep}$ generated by our model.
+The dark solid line represents the distribution of the actual observed data, while the multiple light lines represent the distribution of multiple simulated datasets generated by the model.
+This comparison helps assess the model's fit quality that if the distribution of simulated data $y_{rep}$ closely matches that of the observed data $y$ it then suggests that the model effectively captures the characteristics of the observed data, demonstrating good predictive capability and a reasonable posterior distribution.
+
+In @fig-plot2, we see that the distribution of the simulated data (light lines) aligns closely with the real data distribution (dark line), especially in terms of the peak and shape of the distribution.
+This indicates that the data generated by our model is consistent with the actual data, suggesting that the model can adequately replicate the distributional characteristics of the real data.
+This comparison validates the model's predictive ability and reliability, giving us greater confidence in the model's subsequent predictions.
 
@@
 #| label: fig-post2
-#| fig-cap: "TODO"
+#| fig-cap: PP Check for Model
 #| warning: false
@@
 
+@fig-post3 shows the MCMC sampling trace plots for four key parameters in our model, including the `IVR/Online Panel/Text-to-Web` method variable, the `days_since_Biden_Withdrawal` variable, the error term `sigma`, and the intercept term.
+From Chain 1 to Chain 4, with each chain representing an independent MCMC sampling process.
+Our expectation is that each sampling chain will stabilize and fluctuate around a central value without showing a clear trend (i.e., the mean of the samples converges over time), and there will be no significant differences between the chains.
+If these conditions are met, it indicates that the model has reached convergence, and the posterior distribution is reliable.
+From @fig-post3, we observe that each parameter’s sampling chains display a certain level of stability, with the chains fluctuating around a central value after reaching a steady state, without showing upward or downward trends.
+The distributions across chains are similar, indicating consistency in sampling results and supporting model convergence.
+This suggests that our model has successfully achieved a stable state within the posterior distribution, and the sampling results are reliable.
+
 ```{r, fig.width=5, fig.height=3}
@@
 #| label: fig-post3
-#| fig-cap: "TODO"
+#| fig-cap: MCMC sampling trace plots for model
 #| warning: false
@@
 plot(first_model, "trace", pars = c("methodologyIVR/Online Panel/Text-to-Web", "days_since_Biden_Withdrawal", "sigma", "(Intercept)"))
-
-plot(first_model, "rhat")
 ```
+This plot shows the $\hat{R}$ diagnostic statistic for our model, which is commonly used to assess the convergence of MCMC sampling.
+Ideally, the $\hat{R}$ value should be close to 1, indicating consistent variance across different MCMC chains, signifying that the model has reached a stable state.
+The horizontal axis represents the $\hat{R}$ values, where values closer to 1 indicate better convergence.
+Our expectation is that all parameters have $\hat{R}$ values below 1.05, indicating minimal variance differences between chains and consistency across them.
+This plot shows that nearly all $\hat{R}$ values are concentrated around 1, with all falling below the threshold of 1.05 (indicated by the vertical dashed line on the right), suggesting that the sampling chains have converged well, providing high reliability for the model results.
 
@@
 #| label: fig-post4
+#| fig-cap: "TODO"
+#| warning: false
+
+plot(first_model, "rhat")
+```
+
+@fig-post5 shows the posterior distributions of certain parameters in our model, including the `(Intercept)`, a methodology variable `methodologyIVR/Online Panel/Text-to-Web`, a time variable `days_since_Biden_Withdrawal`, and the error term `sigma`.
+From the shape and location of the posterior distributions, we can see the degree to which the observed data supports the estimates of these parameters and the range of uncertainty around them.
+The `(Intercept)` distribution is centered around 30% to 55%, suggesting that the model estimates a 45% baseline support rate, which aligns with our expectations for Trump’s support rate.
+The methodology variable shows a relatively wide distribution, indicating that the data does not provide strong directional support for its influence, suggesting that it may have a minimal or uncertain impact on the support rate.
+Also, the time variable has a posterior distribution close to zero, indicating that the number of days since Biden’s withdrawal does not significantly impact the support rate.
+The error term `sigma` is at a low level, suggesting that the model views the data as having low volatility and being relatively concentrated.
+Thus, we can conclude that the model effectively captures the significant impact of the baseline support rate but but due to data uncertainty, it struggles to reveal the influence of factors like methodology and time.
+This phenomenon may reflect inconsistencies in the data across different poll methods or limitations in the the sample.
+
+```{r, fig.width=5, fig.height=3}
+#| echo: false
+#| eval: true
+#| label: fig-post5
 #| fig-cap: "TODO"

### 2024-11-01 paper/paper.qmd
wrong cross cite fixed, fig-cap updated

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Demystifying Votes: A Hierarchical Bayesian Model for Predicting the 2024 US Presidential Election"
+subtitle: "Decoding the dynamics and biases behind Trump's Approval Ratings with polling Data"
 author: 
@@
 ```
-@fig-plot2 shows a comparison between the distribution of observed data $y$ and the distribution of simulated data $y_{rep}$ generated by our model.
+@fig-post2 shows a comparison between the distribution of observed data $y$ and the distribution of simulated data $y_{rep}$ generated by our model.
 The dark solid line represents the distribution of the actual observed data, while the multiple light lines represent the distribution of multiple simulated datasets generated by the model.
@@
 
-In @fig-plot2, we see that the distribution of the simulated data (light lines) aligns closely with the real data distribution (dark line), especially in terms of the peak and shape of the distribution.
+In @fig-post2, we see that the distribution of the simulated data (light lines) aligns closely with the real data distribution (dark line), especially in terms of the peak and shape of the distribution.
 This indicates that the data generated by our model is consistent with the actual data, suggesting that the model can adequately replicate the distributional characteristics of the real data.

### 2024-11-01 paper/paper.qmd
fig-caps added

@@
 #| label: fig-post4
-#| fig-cap: "TODO"
+#| fig-cap: R hat Diagnostic statistic for model
 #| warning: false
@@
 #| label: fig-post5
-#| fig-cap: "TODO"
+#| fig-cap: posterior distributions of four parameters in model
 #| warning: false

### 2024-11-02 paper/paper.qmd
1. all /cloud/project/ part in path for writing file or reading file are removed. 2. incorrect link in thanks part of paper changed 3. analysis dataset both saved in parquet file, and according .csv file removed.

@@
   - Chenming Zhao
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder).
+thanks: "Code and data are available at: [https://github.com/ChenmingZ2000/2024-presidential-polls-analysis-and-forecast.git).
         We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis.
@@
 
-analysis_data <- read_parquet(here::here("/cloud/project/data/02-analysis_data/analysis_trump_data.parquet"))
+analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_trump_data.parquet"))
 ```
@@
 
-first_model <- readRDS(file = here::here("/cloud/project/models/trump_time_model.rds"))
+first_model <- readRDS(file = here::here("models/trump_time_model.rds"))
 
-prediction_data <- read_csv(here::here("/cloud/project/data/02-analysis_data/prediction_data.csv"))
+prediction_data <- read_parquet(here::here("data/02-analysis_data/prediction_data.parquet"))
 ```
@@
   fmt = 2,
-  output = here::here("/cloud/project/paper/model_summary_table.html")
+  output = here::here("paper/model_summary_table.html")
 )

### 2024-11-02 scripts/00-simulate_data.R

@@ -52,4 +52,4 @@ political_support
 
 
 #### Save data ####
-write_csv(political_support, "/cloud/project/data/00-simulated_data/simulated_data.csv")
+write_csv(political_support, "data/00-simulated_data/simulated_data.csv")

### 2024-11-02 scripts/01-test_simulated_data.R

@@ -13,7 +13,7 @@
 #### Workspace setup ####
 library(tidyverse)
 
-sample_data <- read_csv("/cloud/project/data/00-simulated_data/simulated_data.csv")
+sample_data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 # Test if the data was successfully loaded
 if (exists("sample_data")) {

### 2024-11-02 scripts/02-clean_data.R

@@ -25,7 +25,7 @@ library(dplyr)
 library(arrow)
 
 #### Clean data ####
-raw_data <- read_csv("/cloud/project/data/01-raw_data/president_polls_raw_data.csv")
+raw_data <- read_csv("data/01-raw_data/president_polls_raw_data.csv")
 
 
 # Filters were used to filter good quality Trump related polls in the dataset
@@ -73,4 +73,4 @@ trump_data <- trump_data %>%
 trump_data$days_since_Biden_Withdrawal <- as.numeric(trump_data$start_date - as.Date("2024-07-21"))
 
 #### Save data ####
-write_parquet(trump_data, "/cloud/project/data/02-analysis_data/analysis_trump_data.parquet")
+write_parquet(trump_data, "data/02-analysis_data/analysis_trump_data.parquet")

### 2024-11-02 scripts/03-test_analysis_data.R

@@ -14,7 +14,7 @@
 library(tidyverse)
 library(testthat)
 
-data <- read_csv("/cloud/project/data/02-analysis_data/analysis_trump_data.csv")
+data <- read_parquet("data/02-analysis_data/analysis_trump_data.parquet")
 
 
 #### Test data ####

### 2024-11-02 scripts/05-model_data.R

@@ -19,7 +19,7 @@ library(rstanarm)
 library(arrow)
 
 #### Read data ####
-analysis_data <- read_parquet("/cloud/project/data/02-analysis_data/analysis_trump_data.parquet")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_trump_data.parquet")
 
 ### Model data ####
 trump_time_series_model <- stan_glmer(
@@ -35,7 +35,7 @@ trump_time_series_model <- stan_glmer(
 #### Save model ####
 saveRDS(
   trump_time_series_model,
-  file = "/cloud/project/models/trump_time_model.rds"
+  file = "models/trump_time_model.rds"
 )
 
 

### 2024-11-02 scripts/06-prediction_data.R

@@ -21,6 +21,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 
 trump_time_series_model <- readRDS("/cloud/project/models/trump_time_model.rds")
 
@@ -70,7 +71,7 @@ prediction_data <- data.frame(
 )
 
 
-# 生成预测值
+# Generating predictions
 prediction_data$methodology <- factor(prediction_data$methodology, levels = levels(trump_data$methodology))
 # Fill missing values in the 'methodology' column with a random sample from valid levels
 prediction_data$methodology[is.na(prediction_data$methodology)] <- sample(
@@ -81,15 +82,15 @@ prediction_data$methodology[is.na(prediction_data$methodology)] <- sample(
 
 prediction_samples <- posterior_predict(trump_time_series_model, newdata = prediction_data)
 
-# 计算预测均值和置信区间
+# Calculate the predicted mean and confidence interval
 prediction_means <- apply(prediction_samples, 2, mean)
 prediction_ci_lower <- apply(prediction_samples, 2, quantile, probs = 0.025)
 prediction_ci_upper <- apply(prediction_samples, 2, quantile, probs = 0.975)
 
-# 将结果添加到数据框
+# Adds the result to the data frame
 prediction_data$predicted_support <- prediction_means
 prediction_data$lower_ci <- prediction_ci_lower
 prediction_data$upper_ci <- prediction_ci_upper
 
 #### Save data ####
-write_csv(prediction_data, "/cloud/project/data/02-analysis_data/prediction_data.csv")
+write_parquet(prediction_data, "data/02-analysis_data/prediction_data.parquet")

### 2024-11-02 paper/paper.qmd
wrong links fixed

@@
   - Chenming Zhao
-thanks: "Code and data are available at: [https://github.com/ChenmingZ2000/2024-presidential-polls-analysis-and-forecast.git).
+thanks: "Code and data are available at: [https://github.com/ChenmingZ2000/2024-presidential-polls-analysis-and-forecast.git](https://github.com/ChenmingZ2000/2024-presidential-polls-analysis-and-forecast.git).
         We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis.

### 2024-11-02 paper/paper.qmd
for prose, all words except "insight" and "reveal" removed or replaced by proper words

@@
 Once the survey is designed, polling begins, and responses are aggregated by the polling organization.
-Respondents' answers are recorded and categorized, converting their opinions into structured data points, though these lack the nuances of human complexity.
+Respondents' answers are recorded and categorized, converting their opinions into structured data points, though these lack of human complexity.
 To protect privacy, data are often anonymized and aggregated, retaining key insights.
@@
 The electoral college system in the U.S.
-makes state-level approval rates crucial for predicting the likelihood of winning.
+makes state-level approval rates important for predicting the likelihood of winning.
 
@@
 
-Although low-frequency observations may introduce some bias, directly removing them would result in information loss, especially in election predictions where the representativeness of different states and pollsters is crucial.
+Although low-frequency observations may introduce some bias, directly removing them would result in information loss, especially in election predictions where the representativeness of different states and pollsters is important.
 Different pollsters and states have their own resources and priorities, leading to uneven data coverage.
@@
 Additionally, we aim to cover as many pollsters and states as possible with the model, so we retain even low-frequency observations.
-Thus, we keep these observations and mitigate the bias they introduce by combining other variables to build a more comprehensive and robust predictive model.
+Thus, we keep these observations and mitigate the bias they introduce by combining other variables to build a more robust predictive model.
 
@@
 
-We implemented the model using the rstanarm package, leveraging MCMC sampling for Bayesian inference.
+We implemented the model using the rstanarm package, using MCMC sampling for Bayesian inference.
 To validate the model, we performed out-of-sample testing and calculated the RMSE (Root Mean Square Error), which resulted in 2.31.
@@
 At the state level, @fig-results shows predictions indicate significant variations between states.
-For example, support in Texas is considerably higher than in California, with a gap of over 10 percentage points, while swing states like Pennsylvania and Michigan display greater volatility.
+For example, support in Texas is considerably higher than in California, with a difference of over 10 percentage points, while swing states like Pennsylvania and Michigan display greater volatility.
 This result further validates the model’s robustness; the introduction of a random intercept for each state reflects systematic differences across states.
@@
 In previous U.S.
-presidential elections, shifts in sentiment in swing states have played a crucial role in determining the outcome.
+presidential elections, shifts in sentiment in swing states have played a important role in determining the outcome.
 For example, the 2016 election highlighted the importance of swing states like Pennsylvania, Michigan, and Wisconsin, where polls underestimated Trump’s support.
@@
 #### The Randomness of the Real World
-Voter preferences can shift rapidly due to events like debates, economic changes, or international incidents, challenging election predictions.
+Voter preferences can shift due to events like debates, economic changes, or international incidents, challenging election predictions.
 Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts.

### 2024-11-02 paper/paper.qmd
abstract and title updated missing citation for package arrow updated

@@
 ---
-title: "Demystifying Votes: A Hierarchical Bayesian Model for Predicting the 2024 US Presidential Election"
-subtitle: "Decoding the dynamics and biases behind Trump's Approval Ratings with polling Data"
+title: "A Hierarchical Bayesian Analysis for Predicting the 2024 US Presidential Election"
+subtitle: "Trump's chances of winning are slim"
 author: 
@@
 date-format: long
-abstract: "This study aims to use a hierarchical Bayesian model to predict whether Donald Trump will win the 2024 U.S.
+abstract: "This study uses a hierarchical Bayesian model to predict whether Donald Trump will win the 2024 U.S.
 presidential election based on support rates.
-By analyzing data of 2024 US presidential general election polls across states, pollsters, and methodologies, we capture variations in support for Trump driven by these factors.
-Our results reveal significant differences in support between national and state-level polls, with fluctuations in key swing states potentially influencing the election outcome.
-There is a dynamic interaction between election results and public opinion trends, and this study provides insights into how various factors influence public sentiment, offering valuable predictions and understanding of voter dynamics in the U.S.
+By analyzing 2024 election data across states, pollsters, and methodologies, we capture the influence of these elements on Trump’s support rate.
+Our prediction shows Trump has little chance to win due to those key swing states that could affect the outcome.
+This study also observes the elements shaping public sentiment and provides predictions on the dynamics of support rates in the U.S.
 election."
@@
 To simulate, test, analyze, and clean the polling data, the statistical programming language R was employed [@citeR].
-Key libraries that supported the data analysis include `tidyverse` [@tidyverse], `readxl` [@readxl], `dplyr` [@dplyr], `knitr` [@knitr], `ggplot2` [@ggplot2], `kableExtra` [@kableExtra] and `patchwork` [@patch].
+Key libraries that supported the data analysis include `tidyverse` [@tidyverse], `readxl` [@readxl], `dplyr` [@dplyr], `arrow` [@arrow], `knitr` [@knitr], `ggplot2` [@ggplot2], `kableExtra` [@kableExtra] and `patchwork` [@patch].
 Additionally, the `rstanarm` [@rstanarm] library was utilized to implement multilevel modeling for prediction purposes.
@@
 ## Model Output
-Our results are summarized in a table which is available [here](https://8360846bf92342d59862bf4ec3515643.app.posit.cloud/file_show?path=%2Fcloud%2Fproject%2Fpaper%2Fmodel_summary_table.html).
+Our results are summarized in a table which is available in @tbl-model.
 This summary reveals the effects of different polling methods and organizations on our estimates.
@@
 #| eval: true
+#| label: tbl-model
+#| tbl-cap: "TODO"
 #| warning: false
@@
 modelsummary::modelsummary(
-  list("First model" = first_model),
+  list("Bayesian model" = first_model),
   statistic = "mad",
   fmt = 2,
-  output = here::here("paper/model_summary_table.html")
+  coef_map = c("(Intercept)", "days_since_Biden_Withdrawal", "is_national", 
+               "methodologyIVR/Online Panel/Text-to-Web", "Sigma[pollster:(Intercept),(Intercept)]",
+               "Sigma[state:(Intercept),(Intercept)]", "Sigma[pollster:days_since_Biden_Withdrawal,days_since_Biden_Withdrawal]",
+               "Sigma[pollster:days_since_Biden_Withdrawal,(Intercept)]", "sigma")
 )

### 2024-11-02 paper/paper.qmd
1. added r script for target pollster NYT 2. modified paper title, subtitle, abstract based on Professor Rohan's comment 3. Appendix about pollster NYT added 4. references updated 5. llm usage updated

@@
 ---
-title: "A Hierarchical Bayesian Analysis for Predicting the 2024 US Presidential Election"
-subtitle: "Trump's chances of winning are slim"
+title: "Bayesian Hierarchical Model Predicts Dim Prospects for Trump's Victory in the 2024 U.S. Presidential Election"
+subtitle: "Key Swing States Expected to Be Decisive Factors"
 author: 
@@
 ## Measurement
+In the real world, people's attitudes toward public policies and political events often fluctuate, and these sentiments are frequently concealed beneath the surface.
+Modern society is rife with interest-driven motives and power struggles, especially at pivotal moments like the 2024 presidential election.
+The emotions, biases, and underlying interests of voters make capturing the true public sentiment all the more urgent.
+Polling thus serves as a window into the public’s mood; it is not merely a quantification of voter intent but also a battleground for election strategy and political capital.
 
-The process of transforming real-world phenomena into structured data typically involves several critical steps, from designing surveys to final data entry.
-First, we identify what needs to be measured.
-In this case, we focus on public opinion regarding the 2024 presidential election, particularly support rates for various candidates.
-It is essential to define the data scope (e.g., national or state level) and key variables—such as polling information (e.g., polling organization, start and end dates), sample details (e.g., sample size and demographics), and candidate details (e.g., candidate name and party affiliation).
+The design process of a poll is laden with considerations.
+The first step is to define the measurement objective.
+Here, we focus on the public’s support for presidential candidates, particularly Donald Trump and Harris.
+However, designing a "neutral" and "scientific" poll is far from straightforward.
+Behind the scenes, various interest groups, aiming to sway the poll results in favor of their supported candidates, subtly influence sample selection, questionnaire design, and survey methodology, embedding "stances" within the poll itself.
 
-Next, polling organizations develop survey questions based on the desired data, considering sample size, sampling methods, and survey modes to capture respondents' preferences and voting intentions.
-Different methodologies impact the results, as they reflect the views of distinct groups, which may be influenced by factors like access channels, demographics, and technology usage.
-For instance, face-to-face surveys tend to capture opinions from offline-inclined groups, whereas voluntary online surveys exclude those less active online.
+When designing the poll, research teams must select an appropriate sampling frame and methodology to ensure that the data represents the broader opinions of the electorate.
+Yet, in a society divided by information access and technology, survey methods can introduce notable biases.
+For instance, face-to-face interviews or telephone surveys reach voters who are less internet-active, while online self-administered questionnaires are more likely to attract digitally savvy young people.
+This variation reflects not only a technical challenge but also a societal layering of bias—who gets represented, who is overlooked, whose voices are amplified, and whose are suppressed.
+These issues are often embedded in the survey’s design from the outset.
 
-Once the survey is designed, polling begins, and responses are aggregated by the polling organization.
-Respondents' answers are recorded and categorized, converting their opinions into structured data points, though these lack of human complexity.
-To protect privacy, data are often anonymized and aggregated, retaining key insights.
-After collection, raw data undergo cleaning and processing to minimize sampling biases and errors.
-Yet, any single poll can have random and systematic error sources, so combining multiple poll results helps mitigate these errors [@blumenthal2010polls].
+Next, the formal data collection phase begins.
+Pollsters must record each voter’s choice in an “impartial” manner, but data collection is often subject to various interferences.
+On one hand, respondents may not be entirely honest, particularly on sensitive political topics; on the other hand, polling organizations themselves may face influence from sponsors or political pressures, subtly adjusting questionnaires or manipulating how survey results are presented.
+Ultimately, public opinions are recorded as cold numbers, yet these numbers harbor significant social and political tensions.
 
-Processed data are entered into structured datasets.
-Ideally, well-formatted polling data are stored as individual records, typically including fields like polling organization, sample size, survey dates, margin of error, candidate support percentages, and methodology description.
-On platforms like FiveThirtyEight, these fields are standardized for ease of comparison and analysis.
-Finally, FiveThirtyEight and similar platforms aggregate these structured records and present them to the public or allow non-commercial research use, with data usually updated as new polls are released.
-This enables analysts and the public to track changes in candidate support, analyze trends, and interpret results.
-An interesting phenomenon, however, is that as election day approaches, poll results often "converge" or "follow" the average, reducing polling error, with evidence suggesting some "final adjustments" in methodology may occur [@blumenthal2010polls].
+Once data collection is complete, polling data are usually anonymized and aggregated to protect respondents’ privacy and produce “objective” statistics.
+However, even pre-processed data still contain random and systematic errors.
+This is why many media outlets and analysis platforms conduct meta-analyses of multiple polls to mitigate the bias of any single poll, aiming to capture a more accurate trend of public sentiment [@blumenthal2010polls].
+
+The processed data are then stored in a structured database, facilitating comparisons across time, regions, and groups.
+On platforms like FiveThirtyEight, this data becomes the basis not only for predicting election outcomes but also for analyzing the ebbs and flows of voter sentiment.
+Notably, Symposium: Polls, Forecasts, and Aggregators suggests that when election day approaches, poll results often “converge” or “gravitate toward the average,” a phenomenon that may suggest that some polling organizations make final adjustments to their methodologies to present a more accurate forecast to the public and their stakeholders [@blumenthal2010polls].
+
+Through this “game” of polling, we not only glimpse voters' preferences and mindsets but also see a microcosm of power and interest battles.
+Polls are more than just numbers—they are a living, breathing social portrait shaped by a multitude of forces.
 
@@
 
-# Additional data details
-
 # Model details {#sec-model-details}
@@
 
-## Diagnostics
+## Pollster Methodology Overview and Evaluation
+### Polling Methods
+Imagine you are watching an orchestra, hoping it will perform seamlessly.
+Every instrument needs to be tuned to just the right pitch so that it combines into a harmonious melody, capturing the audience’s attention and drawing them in.
+This is exactly how polling works—crafting the notes of public opinion into a clear melody that aims to capture and showcase the true views of American voters.
+In this appendix, we focus on The New York Times and Siena College, a pollster that has consistently received the highest rating of 3.0 in recent years from @fivethirtyeight, as the subject of our study and discussion.
+
+Before diving into the specific sampling methods and results, we consider the poll's target population, framework, and sample selection.
+The dataset used in the appendix is from @fivethirtyeight.
+The dataset includes poll results from the middle of 2022 to the present.
+The choice of target population and sample directly impacts the accuracy and relevance of poll results.
+@tbl-polls1 provides an overview of several key components of The New York Times and Siena College poll data.
+From this table, we see that their target population is registered voters (RV), with particular attention given to those likely to vote in the election—likely voters (LV).
+This choice is guided by the goal of predicting election results by focusing on the voter groups that have the greatest influence.
+In actual elections, those with the highest intention to vote often impact the results the most.
+By selecting and focusing on those with strong voting intentions, the poll seeks to ensure that the results are more representative and predictive.
+By concentrating on these "likely voters," the poll aims to mirror the actual composition of voters, providing a forecast closer to the election scenario.
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+
+ny_data <- read_parquet(here :: here("data/02-analysis_data/pollster_data.parquet"))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| label: tbl-polls1
+#| tbl-cap: TODO
+
+kable(head(ny_data, 6), 
+      col.names = c("pollster_name", "538_numeric_grade", "methodology", "population"), 
+      align = c("l", "c", "c", "c")) %>%
+kable_styling(font_size = 8)
+
+```
+
+After selecting the target population, the next step is determining the polling framework.
+From @nytimes2018pollmethod, we can see that the phone numbers for The New York Times and Siena College poll samples come from national voter files and market research companies.
+Specifically, the polling team collaborates with L2, extracting samples from the national voter file and supplementing them with matching cell phone numbers provided by Marketing Systems Group to create a database of phone contacts.
+The purpose of these dual information sources is to allow the poll to gather more complete contact information.
+Once the phone numbers are obtained, the polling team randomly dials both cell phones and landlines, using the different contact methods to reach diverse groups.
+Combined, these methods provide a broader, more inclusive view of public opinion.
+This process is known as a dual-frame approach.
+
+In sampling, The New York Times and Siena College employ stratified sampling, dividing voters by characteristics such as race, party affiliation, and region [see @nytimes2024methodology].
+The purpose of stratified sampling is to ensure that each significant voter subgroup is appropriately represented in the final sample, capturing the diversity of the population and preventing the poll from lacking representativeness or being biased.
+Imagine a jigsaw puzzle, where each group is like a puzzle piece that must fit perfectly within the whole to form a complete picture.
+Of course, finding the right "pieces" and placing them in the correct spots requires careful planning.
+The polling team relies on accurate and up-to-date demographic data, a challenge that demands extensive resources and attention to detail.
+
+Then there is population weighting and the voter likelihood model.
+To make the sample more reflective of the actual voting population, the team takes into account past voting behavior, demographic characteristics, and respondents' self-reported voting intention.
+This adjustment gives more weight to the feedback from those who are likely to vote.
+In essence, this model fine-tunes the sample to better align with real voting patterns.
+However, much like a conductor shaping a new season’s performance based on the last, this model relies on past data, which may overlook new trends or unexpected changes in behavior [see @nytimes2018pollmethod].
+
+Finally, it goes to question design.
+Like lyrics in a song, each question needs to encourage respondents to share their genuine opinions, avoiding wording that could sway answers.
+The New York Times and Siena College publish every question verbatim, allowing anyone to see exactly what was asked.
+Like an open rehearsal, this transparency builds trust.
+The questions are clear and aim to remain neutral, though the simplicity can sometimes limit depth, missing subtle aspects in complex topics.
+
+### Challenges and New York Times' Response
+
+One challenge that arises in polling is that, despite the careful design aimed at ensuring broad coverage, not everyone is willing to participate.
+This is known as the **nonresponse issue**.
+To make the results more representative, pollsters at The New York Times and Siena College make multiple attempts to contact individuals.
+However, despite these efforts, the overall response rate remains around 2%, which is relatively low.
+This low rate naturally raises curiosity about how those who stay silent might view the issues.
+In 2022, an experiment aimed at measuring the impact of nonresponse on their phone surveys suggested that the resulting bias might not be substantial.
+However, The New York Times also acknowledges, “the truth is that there’s no way to be absolutely sure that the people who respond to surveys are like demographically similar voters who don’t respond.
+It’s always possible that there’s some extra dimension of nonresponse that we haven’t considered” [see @nytimes2024methodology].
+
+We are concerned about how feedback from around 1,000 people can represent the entire United States.
+To address this question, The New York Times uses the analogy of “tasting a soup with just one spoonful.” They argue that their method includes a sufficiently random sample, noting that if they were to double—or even triple—the number of respondents, the margin of error would only slightly decrease, possibly by about two percentage points.
+In other words, increasing the sample size would not greatly improve overall accuracy.
+The New York Times explains that once the survey is complete, they compare respondents to voter files and use a process known as weighting to ensure the sample reflects the broader voting population.
+In practice, this often means giving more weight to groups less likely to participate in surveys, such as those without a college degree [@nytimes2024methodology] [@nytimes2022wisconsin].
+
+Then there’s the voter likelihood model.
+In the NYT/Siena poll, they use information from voter files to review each voter’s voting history, using past behavior to predict future voting patterns.
+They also ask respondents about their likelihood to vote and use this information to estimate how likely someone is to vote in the upcoming election.
+However, much like a conductor adjusts a new season’s performance based on the previous one, this model relies on past data, which might miss new trends or unexpected changes in behavior.
+The New York Times itself mentions that the margin of error in its polls ranges between 2% and 4%, a factor that could play a decisive role in a close election [see @nytimes2024methodology].
+
+Additionally, even with the best planning, The New York Times notes that they ensure the correct number of interviews by race, party, and region so that each NYT/Siena poll reaches, for example, the appropriate proportion of white Democrats from the West, or Hispanic Republicans from Maricopa County, Arizona [@nytimes2024methodology] [@nytimes2022wisconsin].
+Still, some groups remain difficult to reach.
+Pollsters attempt to compensate for this by adjusting sample weights, but weighting itself introduces challenges.
+If certain groups are over- or under-adjusted within the sample, it may destabilize results and obscure potential sample limitations.
 

### 2024-11-02 scripts/06-prediction_data.R

@@ -8,7 +8,7 @@
 # Contact: chenming.zhao@mail.utoronto.ca
 # License: MIT
 # Pre-requisites:
-#   - Install the necessary libraries: `tidyverse`, `rstanarm`.
+#   - Install the necessary libraries: `tidyverse`, `arrow`.
 #   - Ensure the Trump time series model is available at "/cloud/project/models/trump_time_model.rds".
 #   - Have a folder structure set up with the data directory "/cloud/project/data/02-analysis_data/"
 #     to save the prediction output.
@@ -23,7 +23,7 @@
 library(tidyverse)
 library(arrow)
 
-trump_time_series_model <- readRDS("/cloud/project/models/trump_time_model.rds")
+trump_time_series_model <- readRDS("models/trump_time_model.rds")
 
 trump_data$methodology <- as.factor(trump_data$methodology)
 

### 2024-11-02 scripts/07-New_York_Times_pollster.R

@@ -1,0 +1,36 @@
+#### Preamble ####
+# Purpose: 
+# Author: Chenming Zhao
+# Date: 2 November 2024
+# Contact: chenming.zhao@mail.utoronto.ca
+# License: MIT
+# Pre-requisites:
+#   - Install the necessary libraries: `tidyverse`, `rstanarm`.
+#   - Ensure the Trump time series model is available at "/cloud/project/models/trump_time_model.rds".
+#   - Have a folder structure set up with the data directory "/cloud/project/data/02-analysis_data/"
+#     to save the prediction output.
+# Any other information needed:
+#   - This script assumes the structure of `trump_data` is consistent with the input model 
+#     used to create `trump_time_series_model`.
+#   - The output CSV file ("prediction_data.csv") contains support rate predictions, including
+#     point estimates and 95% credible intervals, to be used for further analysis or visualization.
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+library(arrow)
+
+#### Load data ####
+data <- read_csv("data/01-raw_data/president_polls_raw_data.csv")
+
+ny_data <- data %>% 
+  mutate(start_date = as.Date(end_date, format = "%m/%d/%y")) %>%
+  filter(display_name == "The New York Times/Siena College") %>%
+  distinct()
+
+ny_data <- ny_data %>% select("display_name", "numeric_grade", "methodology", "population")
+
+
+#### Save data ####
+write_parquet(ny_data, "data/02-analysis_data/pollster_data.parquet")

### 2024-11-02 paper/paper.qmd
llm usage updated for generation of reference reference updated for poll texas Appendix advantage and disadvantage of poll updated

@@
 
-Additionally, even with the best planning, The New York Times notes that they ensure the correct number of interviews by race, party, and region so that each NYT/Siena poll reaches, for example, the appropriate proportion of white Democrats from the West, or Hispanic Republicans from Maricopa County, Arizona [@nytimes2024methodology] [@nytimes2022wisconsin].
+Additionally, even with the best planning, the New York Times notes that they ensure the correct number of interviews by race, party, and region so that each NYT/Siena poll reaches, for example, the appropriate proportion of white Democrats from the West, or Hispanic Republicans from Maricopa County, Arizona [@nytimes2024methodology] [@nytimes2022wisconsin].
 Still, some groups remain difficult to reach.
@@
 
+### The Advantages and Disadvantages of the Questionnaire Design
+
+From polls like @nytimes2024texaspoll, the NYT/Siena polls maintain a high level of transparency, with each survey report publishing the questionnaire verbatim.
+This approach allows both the public and researchers to clearly understand the questions asked, enhancing trust.
+The questions are also straightforward, avoiding complex wording, which reduces the risk of misunderstandings across different respondent groups and improves response accuracy.
+Furthermore, the language is kept neutral, avoiding any leading phrases.
+This neutrality helps prevent bias that might arise from the phrasing of questions, ensuring that respondents’ answers are based on their genuine views rather than being influenced by question design, which supports the objectivity of the results.
+
+The questionnaire is designed to examine respondents’ multifaceted characteristics, covering not only basic demographics like age, gender, and education level but also other personal traits and preferences.
+This information helps analyze political opinion differences across diverse backgrounds, making the results more representative.
+For example, the questionnaire may include questions on race, occupation, or top priorities when choosing a president—factors that often significantly impact voting preferences.
+It also includes questions about respondents' group characteristics, such as geographic location, community type (urban or rural), and political affiliation.
+By covering these factors, the survey can accurately reflect differences in public opinion across different regions and social environments.
+In a politically polarized climate, this detailed grouping helps identify regional or community-specific trends, showing how voters from different backgrounds feel about candidates or policies.
+
+The questionnaire also includes questions about religious beliefs to analyze the impact of religion on voting intentions.
+Religious affiliation often aligns closely with political views, particularly in the U.S., where religious beliefs can strongly influence positions on morality, social policies, and party preferences.
+By incorporating religious affiliation, the questionnaire can better capture how religion influences voter choices, allowing for more targeted analysis of various religious backgrounds.
+
+However, certain aspects of the questionnaire design have limitations.
+For instance, to keep questions concise, the survey may not delve deeply into complex topics, possibly overlooking subtle but important perspectives.
+For example, questions about voting likelihood are sometimes too general; each respondent may interpret “likelihood” differently based on their personal standards.
+Additionally, the lack of open-ended questions limits the depth of responses, reducing the questionnaire's ability to capture detailed opinions.
+
+Another limitation is the focus on mainstream religions, often overlooking other groups such as Islam, Hinduism, Buddhism, and Sikhism.
+With increasing immigration, the number of voters from these religious backgrounds is rising, and their political preferences may differ from those of traditional religious groups.
+For instance, Muslim, Hindu, or Buddhist voters may prioritize issues such as cultural diversity, foreign policy, or religious freedom differently.
+The absence of questions covering these religions may result in a poll that does not fully reflect the priorities of all voters, limiting its representativeness.
+It also makes it harder to track the growing influence and political leanings of these groups.
+Without including these religious backgrounds, the questionnaire may miss important shifts in political attitudes among these emerging voter groups, potentially losing opportunities for future research.
+
+The question in The Times/Siena Poll: Texas Topline, “If you had to decide between the two today, would you lean more toward” saw a high rate of “Don’t know/Refused” responses, at 66% [see @nytimes2024texaspoll].
+This likely reflects a sense of dissatisfaction among voters due to political polarization.
+Many voters may feel discontent with both major candidates (Trump and Harris) and, as a result, choose not to respond when dissatisfied with the options or disillusioned with the political landscape.
+Additionally, the phrasing, “if you had to decide between the two today,” may make respondents feel pressured, leading to a refusal to answer.
+For those inclined toward third-party candidates or undecided voters, this type of question may further discourage responses.
+This question specifically targeted “leaners” (respondents who previously did not clearly support either Trump or Harris), often representing “swing” or “undecided” voters.
+Asking these voters, who are inherently unsure, to make a decision without strong support for either candidate could contribute to the high rate of refusals.
+A similar pattern is observed in questions like “(Leaners, if no candidate selected in initial multi-candidate question) If you had to decide today, would you lean more toward,” where respondents also frequently chose “Don’t know/Refused.”
+
 \newpage

### 2024-11-04 paper/paper.qmd
reference added for swing states data part missing plot for variables added result part changed for more reliable results

@@
         We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis.
-The data is available at: [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/)."
+The data is available at: [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/).
+        Our survey for the 2024 U.S.
+presidential election is available at : [https://docs.google.com/forms/d/1GI7KoltEKEdmZNfNorXxjvapUd_s2obJyRNrMYsjndw/prefill](https://docs.google.com/forms/d/1GI7KoltEKEdmZNfNorXxjvapUd_s2obJyRNrMYsjndw/prefill)"
 date: today
@@
 By analyzing 2024 election data across states, pollsters, and methodologies, we capture the influence of these elements on Trump’s support rate.
-Our prediction shows Trump has little chance to win due to those key swing states that could affect the outcome.
+Our prediction shows Trump has little chance to win due to He will not have higher support rate in key swing states than Harris.
 This study also observes the elements shaping public sentiment and provides predictions on the dynamics of support rates in the U.S.
@@
 
+@fig-pct3 shows the differences in Trump’s support rate distribution between national and state-level polls.
+National polls have a more concentrated support rate, ranging approximately between 45% and 55%, with a median slightly lower than that of state-level polls, indicating a more stable level of support across the country.
+In contrast, state-level polls show a wider range of support, fluctuating from around 35% to over 60%, highlighting notable variations in support across different states.
+Additionally, state-level polls display more outliers, further reflecting the uneven support rate among states.
+
 ```{r, message=FALSE, fig.width=6, fig.height=3}
 #| label: fig-pct1
-#| fig-cap: Support rates for Donald Trump which showed in different variables plot 1
+#| fig-cap: Top 5 and Bottom 5 Avg Support Rate for Donald Trump by pollsters (left) and by states with national included (right)
 #| echo: false
@@
 #| label: fig-pct2
-#| fig-cap: Support rates for Donald Trump which showed in different variables plot 2
+#| fig-cap: Average Support Rate  for Donald Trump from 2024-07-21 to 2024-10-23 reported by different pollsters
 #| echo: false
@@
 
+```{r, message=FALSE, fig.width= 4, fig.height= 3}
+#| label: fig-pct3
+#| fig-cap: National support rate and state level support rate for Donald Trump 
+#| echo: false
+
+ggplot(analysis_data, aes(x = factor(is_national, levels = c(0, 1), labels = c("State Polls", "National Polls")), 
+                 y = pct)) +
+  geom_boxplot() +
+  labs(x = "Poll Type", y = "Trump Support Rate (%)", title = "Support Rate by Poll Type (National vs. State)") +
+  theme_minimal()
+```
+
 # Model {#sec-model}
@@
 
-```{r}
+```{r, message=FALSE}
 #| echo: false
@@
 #| label: tbl-model
-#| tbl-cap: "TODO"
+#| tbl-cap: Model summary table for model which predicts support rate for Donald Trump in 2024 presidential election 
 #| warning: false
@@
 ## Prediction Output
-From @fig-results, the model predicts that nationwide support for Trump on Election Day, November 5, 2024, will center between 45% to 50% and shows moderate fluctuations.
-This variability is mainly attributed to national events and differences in polling methods.
-For instance, nationwide events such as economic shifts or unexpected political occurrences may influence voter sentiment, while differences in polling methods (such as phone surveys versus online panels) may introduce slight fluctuations in estimates due to differences in sample coverage.
-
-At the state level, @fig-results shows predictions indicate significant variations between states.
-For example, support in Texas is considerably higher than in California, with a difference of over 10 percentage points, while swing states like Pennsylvania and Michigan display greater volatility.
-This result further validates the model’s robustness; the introduction of a random intercept for each state reflects systematic differences across states.
-This design aligns with data trends, suggesting that states with diverse geographic and demographic profiles exhibit unique political tendencies.
-
-```{r, fig.width=5, fig.height=5}
+The swig states information is from @270toWin.
+@fig-results shows that states with similar demographic characteristics (such as Pennsylvania and Michigan) exhibit comparable fluctuations in support rates.
+It also indicates that the model predicts Trump’s national support rate on Election Day, November 5, 2024, to center around 45% to 50%, with moderate variation.
+This suggests that despite the influence of national events and polling method differences, the national support rate remains relatively stable, reflecting a steady stance among most voters.
+We forecast that Trump’s national average support rate will be below 50%.
+
+At the state level, the chart reveals variations in support rates among states, with swing states other than Arizona and North Carolina tending to show average support rates below 50%.
+Swing states like Pennsylvania and Michigan display significant volatility, as indicated by wider interquartile ranges and multiple outliers in the box plot.
+This volatility suggests that voter preferences in these states are less stable, and support rates in competitive states are more susceptible to minor events or policy shifts.
+Therefore, we predict Trump’s support rate in swing states other than Arizona and North Carolina will remain below 50%.
+
+As key factors in the election, this forecast data, combined with Harris’s lead, suggests that Trump’s chance of winning 2024 presidential election is slim.
+
+```{r, fig.width=5, fig.height=4}
 #| echo: false
@@
 #| warning: false
-national_only <- prediction_data[prediction_data$state == "national", ]
-all_states <- prediction_data[prediction_data$state != "national", ]
-
-p4 <- ggplot(national_only, aes(x = state, y = predicted_support)) +
-  geom_point(size = 3, color = "lightblue") +
-  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "lightblue") +
-  labs(title = "Election Day National Trump Support Rate Prediction", y = "Predictied Support Rate (%)", x = "Area Type in US") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(size = 7),
-    axis.text.y = element_text(size = 6),
-    plot.title = element_text(size = 8, face = "bold", color = "#333333"),
-    axis.title = element_text(size = 7, color = "#333333"))
+
+swing_states <- c("Arizona", "Nevada", "Michigan", "Wisconsin", "Pennsylvania", "North Carolina", "national")
+need_states <- prediction_data[prediction_data$state %in% swing_states, ]
 
 # Plot for state data
-p5 <- ggplot(all_states, aes(x = state, y = predicted_support)) +
-  geom_jitter(size = 3, color = "lightblue", width = 0.3) +  # Adds slight horizontal jitter to reduce overlap
+ggplot(need_states, aes(x = state, y = predicted_support)) +
+  geom_boxplot(color = "lightblue") +  # Adds slight horizontal jitter to reduce overlap
   geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "lightblue", alpha = 0.6) +
-  geom_smooth(aes(group = 1), method = "lm", color = "orange", se = FALSE) +  # Adds a trend line across all states
   geom_hline(yintercept = 50, color = "black", linetype = "dashed", size = 0.7) +  # Adds a reference line at 50%
   scale_y_continuous(breaks = seq(0, 70, by = 10)) +  # Formats y-axis as percentages with 1 decimal precision
-  labs(title = "Election Day Trump Support Rate Prediction by State", y = "Predictied Support Rate (%)", x = "States") +
+  labs(title = "Election Day Trump Support Rate Prediction Both Nation and Swing States Icluded", y = "Predictied Support Rate (%)", x = "States") +
   theme_minimal() +
@@
 
-p4 + p5 + plot_layout(nrow = 2)
 ```
@@
 
-## Pollster Methodology Overview and Evaluation
+# Pollster Methodology Overview and Evaluation
 ### Polling Methods
@@
 ### Challenges and New York Times' Response
-
 One challenge that arises in polling is that, despite the careful design aimed at ensuring broad coverage, not everyone is willing to participate.
@@
 
+# Methodology and Survey Design
+
+To design an effective survey method, we will begin by defining our target population and sampling framework.
+Our survey will target both **likely voters (LV)**, those who have a high intention of voting, and **registered voters (RV)**.
+Likely voters provide more accurate election predictions by focusing on those most likely to participate.
+However, registered voters, including those with lower voting intentions, also represent broader social and political attitudes.
+Including them ensures the survey reflects not only who is likely to win but also captures societal perspectives on what defines a presidential candidate.
+
+To ensure representativeness, we will use **stratified random sampling**.
+The sample will be divided by age, race, education, income level, and region.
+This approach allows selective, representative sampling within key groups, reducing sampling bias and improving reliability.
+
+With a budget of $100,000, we plan to survey approximately 1,500 respondents, covering these demographic groups.
+Based on The New York Times' experience, this sample size is sufficient to represent the overall picture of the United States [see @nytimes2024methodology].
+We aim to keep the margin of error around 2%-4% while ensuring the representativeness of each subgroup, creating a snapshot of U.S.
+society within the election context.
+
+Based on the polling methodology of [@nytimes2024methodology], we’ll combine email and phone outreach and provide small incentives (about five dollars to ten dollars) to encourage participation and reduce non-response problem.
+Additionally, we plan to work with trusted panel providers, such as YouGov or Dynata, using certified voter panels that align with our target population.
+
+For the survey itself, we will use Google Forms as the platform.
+Familiarity with this platform makes respondents less likely to resist or question the survey.
+It offers ease of access, cost-effectiveness, and reliable data collection.
+Questions will be crafted with clear and neutral wording, allowing respondents to understand the questions without any influence from suggestive language.
+The survey will mostly consist of closed-ended questions and scaled questions to quantify preferences, making the data easier to analyze.
+Additionally, the survey will include one or two open-ended questions, allowing respondents to share their main concerns or factors influencing their choices.
+This setup captures responses that are difficult to summarize or quantify but are important for context.
+
+After data collection, we will proceed with data cleaning.
+First, responses will be cross-verified with national voter files to ensure that respondents are registered voters, filtering out responses from non-voters.
+Each response will be tagged with a unique identifier (such as survey ID) to prevent duplicates.
+After cleaning, we will apply weighting based on age, race, education, and region to align the sample structure with the overall voting population.
+
+Our budget will be allocated as follows:
+
+- Approximately $50,000 for panel partnerships and respondent incentives.
+
+- Around $15,000 for voter file cross-verification, data cleaning, and weighting.
+
+- $20,000 for poll aggregation, regression modeling, and consultation with election analysts.
+
+- $15,000 for staffing, platform fees, and survey testing.
+
+Our survey is available [here](https://docs.google.com/forms/d/1GI7KoltEKEdmZNfNorXxjvapUd_s2obJyRNrMYsjndw/prefill)
+
 \newpage

### 2024-11-04 paper/paper.qmd
prose problem fixed discussion part more edited sketch for is_national and pct uploaded

@@
 By incorporating variables such as days since Biden’s withdrawal, polling methodology, and whether the poll is national or state-level, the model provides a dynamic view of Trump’s support rate across time and place.
-With an R² of 0.641 and an RMSE of 2.31, the model effectively captures these patterns while maintaining predictive accuracy, indicating that it can provide meaningful insights into regional and national public opinion trends.
+With an R² of 0.641 and an RMSE of 2.31, the model effectively captures these patterns while maintaining predictive accuracy, indicating that it can provide a reliable prediction for regional and national public opinion trends.
 Finally, we simulate data for Election Day on November 5 to provide a reliable basis for predicting the election outcome.
 
-Our analysis reveals that differences in Trump’s support rate across regions and polling methods are particularly pronounced.
+Our analysis shows that differences in Trump’s support rate across regions and polling methods are particularly pronounced.
 For example, support rates in traditionally conservative states like Texas differ significantly from those in traditionally liberal states like California, while trends in swing states such as Pennsylvania and Michigan are more unstable, with the potential to disrupt the election balance.
-This underscores the critical impact of geographic and methodological factors on public opinion, aligning well with the historical tendency of swing states to determine the election outcome.
+This underscores the impact of geographic and methodological factors on public opinion, aligning well with the historical tendency of swing states to determine the election outcome.
 Additionally, our results suggest that polling methodologies introduce systematic differences in support rate estimation, with slight variations between results from online panels and phone surveys.
@@
 By modeling the fluctuations in Trump’s support rate, we can infer his electoral performance, and assess the impact of various factors on his popularity.
-Understanding these dynamics provides insights into Trump’s standing relative to his opponents and supports our overall election prediction.
+Understanding these dynamics supports our overall election prediction.
 
@@
 
-```{r, message=FALSE, fig.width= 4, fig.height= 3}
+```{r, message=FALSE, fig.width= 5, fig.height= 3}
 #| label: fig-pct3
@@
   labs(x = "Poll Type", y = "Trump Support Rate (%)", title = "Support Rate by Poll Type (National vs. State)") +
-  theme_minimal()
+  theme_minimal() + theme(
+    axis.text.x = element_text(size = 6),
+    axis.text.y = element_text(size = 5),
+    plot.title = element_text(size = 7, face = "bold", color = "#333333"),
+    axis.title = element_text(size = 6, color = "#333333"),
+  )
 ```
@@
 
-The linear component of the model is defined as follows:
+The linear component of the model is defined as follows (here $\mathrm{days\_since\_Biden\_Withdrawal}$ is shortened to DSBW):
 
 $$
-\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i+ \beta_2 \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i \\
-       + \beta_3 \cdot \mathrm{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \mathrm{days\_since\_Biden\_Withdrawal}_i)
+\mu_i = \alpha + \beta_1 \cdot \text{methodology}_i+ \beta_2 \cdot \mathrm{DSBW}_i \\
+\\
+       + \beta_3 \cdot \mathrm{is\_national}_i + u_{\text{state}[i]} + (v_{\text{pollster}[i]} + \gamma_{\text{pollster}[i]} \cdot \mathrm{DSBW}_i) \\
 $$
@@
 Through the `is_national` variable, we distinguish between national and state-level polls, this variable enables the model to capture support rate differences arising from geographic and demographic differences.
-We expect that national polls, which typically have larger and more representative samples, are better suited to capturing overall trends, while state-level polls may reflect finer, localized biases and specific regional issues because national polls often encompass a broader and more balanced voter base, they provide a more stable forecast of overall voter trends.
+We expect that national polls, which typically have larger and more representative samples, are better suited to capturing overall trends, while state-level polls may reflect finer, localized biases and specific regional issues because national polls often include a broader and more balanced voter base, they provide a more stable forecast of overall voter trends.
 In contrast, due to geographic and demographic variations, state-level polls often exhibit greater fluctuations in error than national polls.
@@
 Our results are summarized in a table which is available in @tbl-model.
-This summary reveals the effects of different polling methods and organizations on our estimates.
+This summary shows the effects of different polling methods and organizations on our estimates.
 For instance, there is a small difference in estimates between data collected via online panels and phone surveys.
@@
 We forecast that Trump’s national average support rate will be below 50%.
-
-At the state level, the chart reveals variations in support rates among states, with swing states other than Arizona and North Carolina tending to show average support rates below 50%.
+At the state level, @fig-results shows variations in support rates among swing states, with swing states other than Arizona and North Carolina tending to show average support rates below 50%.
 Swing states like Pennsylvania and Michigan display significant volatility, as indicated by wider interquartile ranges and multiple outliers in the box plot.
 This volatility suggests that voter preferences in these states are less stable, and support rates in competitive states are more susceptible to minor events or policy shifts.
-Therefore, we predict Trump’s support rate in swing states other than Arizona and North Carolina will remain below 50%.
-
-As key factors in the election, this forecast data, combined with Harris’s lead, suggests that Trump’s chance of winning 2024 presidential election is slim.
 
@@
 presidential election on November 5, 2024, against his primary opponent, Harris.
-The first chart shows the national support rate prediction for Trump, centering around 45% to 50%.
+@fig-results shows the national support rate prediction for Trump, centering around 45% to 50%.
 Historically, any candidate needs to reach or exceed the 50% threshold to secure a decisive victory.
-The current predictions reveal some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with some possibility of winning.
-
-The @fig-results also illustrates the support rates at the state level, revealing significant differences between red and blue states.
-For instance, Trump’s predicted support rate is higher in traditionally conservative states such as Texas, while in strong Democratic states like California, his support rate is lower.
-In swing states like Pennsylvania and Michigan, the support rate hovers around 50%, aligning with historical trends where these states tend to have close contests.
-
-To draw final conclusions from these predictions, it is essential to consider historical polling data and past election results.
-In previous U.S.
-presidential elections, shifts in sentiment in swing states have played a important role in determining the outcome.
+The current predictions show some level of uncertainty, although minor shifts in voter sentiment might occur leading up to Election Day, leaving Trump with some possibility of winning.
+
+The @fig-results also illustrates the support rates at the state level.
+In swing states like Pennsylvania and Michigan, the support rate mostly under 50%, aligning with historical trends where these states tend to have close contests but have big influence on the final election results.
+We predict Trump’s support rate in swing states other than Arizona and North Carolina will remain below 50%.
+Therefore, as important factors in the election, this forecast data, combined with Harris’s lead, suggests that Trump’s chance of winning 2024 presidential election is slim.
+
+We draw final decision based on previous U.S.
+presidential elections, where shifts in sentiment in swing states have played a important role in determining the outcome.
 For example, the 2016 election highlighted the importance of swing states like Pennsylvania, Michigan, and Wisconsin, where polls underestimated Trump’s support.
 A study by the Pew Research Center noted that last-minute sentiment shifts and polling errors led to an unexpected advantage for Trump [@pew2021pollinglimitations].
-Studies by *The Economist* emphasize the critical impact of swing states on election outcomes, also noting that national polls do not always reflect the dynamics of the Electoral College [see @economist2020electionforecast].
+Studies by *The Economist* emphasize the important impact of swing states on election outcomes, also noting that national polls do not always reflect the dynamics of the Electoral College [see @economist2020electionforecast].
 The Electoral College system can result in a candidate winning the popular vote but losing the election, or vice versa.
@@
 For example, relying on historical patterns from states with limited data may fail to reflect the latest shifts in voter sentiment.
-This issue is also seen across different polling organizations and survey methods.
-As @gelman2020regression noted, the model can fluctuate between overconfidence and unreasonable uncertainty.
-To address this, we could consider incorporating alternative data sources, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas.
+To address this, we could consider incorporating alternative data sources in future, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas.
 However, these sources carry their own issues, as they may lack reliability and rigor.
 
-Then, in handling systematic bias introduced by different polling methods, the model accounts for variance by assigning specific variance parameters for each method (e.g., phone interviews vs.
+Similar problem is also seen across different polling organizations and survey methods.
+In handling systematic bias introduced by different polling methods, the model accounts for variance by assigning specific variance parameters for each method (e.g., phone interviews vs.
 online panels).
@@
 In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases.
-For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump [see @pew2024electionpolling and @stanford2020electionpolling].
+For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases [see @pew2024electionpolling and @stanford2020electionpolling].
 
@@
 states.
-Polling each state comprehensively is costly, especially in low-population states or states deemed "safe" for one candidate.
+Polling each state is costly, especially in low-population states or states deemed "safe" for one candidate.
 In these cases, data scarcity means the model largely relies on data from more populous or swing states, which may not fully represent the diversity of the nationwide electorate, introducing potential biases.
@@
 states, multiple polling organizations, and various survey methodologies.
-If we attempted to display every detail within a chart, the visualizations would become overwhelmingly complex, making it difficult for readers to extract key insights.
+If we attempted to display every detail within a chart, the visualizations would become overwhelmingly complex, making it difficult for readers to read or understand.
 Conversely, if we limit the display to a subset, such as only highlighting key states or selected polling methods, this approach risks losing the completeness of information.
@@
 The error term `sigma` is at a low level, suggesting that the model views the data as having low volatility and being relatively concentrated.
-Thus, we can conclude that the model effectively captures the significant impact of the baseline support rate but but due to data uncertainty, it struggles to reveal the influence of factors like methodology and time.
+Thus, we can conclude that the model effectively captures the significant impact of the baseline support rate but but due to data uncertainty, it struggles to catch the influence of factors like methodology and time.
 This phenomenon may reflect inconsistencies in the data across different poll methods or limitations in the the sample.
